### 2016-04-02 paper.tex
Merge the template and the talk code.

% Based on the template for sigplanconf LaTeX Class by Paul C. Anagnostopoulos (paul@windfall.com)
\documentclass[preprint]{sigplanconf}

\usepackage{amsmath}

\newcommand{\cL}{{\cal L}}

\begin{document}

\special{papersize=8.5in,11in}
\setlength{\pdfpageheight}{\paperheight}
\setlength{\pdfpagewidth}{\paperwidth}

\conferenceinfo{FARM 2016}{September 24, 2016, Nara, Japan}
\copyrightyear{2016}
%\copyrightdata{978-1-nnnn-nnnn-n/yy/mm}
%\copyrightdoi{nnnnnnn.nnnnnnn}

\title{Algomusicology, ?, Profit}
%\subtitle{Subtitle Text, if any}

\authorinfo{Chris Ford}
           {ThoughtWorks}
           {christophertford@gmail.com}

\maketitle

\begin{abstract}
This is the text of the abstract.
\end{abstract}

%\category{CR-number}{subcategory}{third-level}

\keywords
keyword1, keyword2

\section{Introduction}

\begin{verbatim}
(ns kolmogorov-music.talk
  (:require [clojure.repl :as repl]
            [midje.sweet :refer :all :exclude [after]]
            [overtone.live :refer :all :exclude [stop]]
            [leipzig.melody :refer :all]
            [leipzig.canon :as canon]
            [leipzig.scale :as scale]
            [leipzig.live :as live]
            [leipzig.live :refer [stop]]
            [leipzig.chord :as chord]
            [leipzig.temperament :as temperament]
            [kolmogorov-music.geb :as geb]
            [kolmogorov-music.coding :as coding]))

;;;;;;;;;;;;;;;;;;;;;;;;;;;;
;;; Air on the \G String ;;;
;;;;;;;;;;;;;;;;;;;;;;;;;;;;

(comment (take 10000 (repeat (* 1000 1000 1000 1000) \G)))

(defmacro description-length [expression]
  (-> expression print-str count))

(defn result-length [expression]
  (-> expression print-str count))

(fact "The description-length is how long the string representation of the expression is."
  (description-length (repeat 65 \G)) => 13)

(fact "The result-length is how long the string representation of the evaluated result is."
  (result-length (repeat 65 \G)) => 131)

(defmacro randomness [expression]
  `(/ (description-length ~expression) (result-length ~expression)))

(fact "Kolmogorov randomness is the compression ratio between the description and the result."
  (randomness (repeat 65 \G)) => 13/131
  (randomness (->> 71 char repeat first)) => 26)

;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;
;;; Analysis by compression ;;;
;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;

(def row-row
  "A simple melody built from durations and pitches."
              ; Row, row, row  your boat,
  (->> (phrase [3/3  3/3  2/3  1/3  3/3]
               [  0    0    0    1    2])
       (then
                ; Gent-ly   down the  stream,
         (phrase [2/3  1/3  2/3  1/3  6/3]
                 [  2    1    2    3    4]))
       (then    ; Merrily, merrily, merrily, merrily,
         (phrase (repeat 12 1/3)
                 (mapcat (partial repeat 3) [7 4 2 0])))
       (then
                ; Life is   but  a    dream!
         (phrase [2/3  1/3  2/3  1/3  6/3]
                 [  4    3    2    1    0]))
       (canon/canon (canon/simple 4))
       (where :pitch (comp scale/A scale/major))))

(comment
  (live/play row-row)
  (live/jam (var row-row))
)

(defmacro definitionally [macro sym]
  (let [value (-> sym repl/source-fn read-string last)]
    `(~macro ~value)))

(fact "The definitionally macro lets us calculate on the definition of symbols."
  (definitionally description-length row-row) => 281
  (definitionally result-length row-row) => 2037
  (definitionally randomness row-row) => 281/2037)

;;;;;;;;;;;;;;;;;;;;;;;;;;;;
;;; The Library of Babel ;;;
;;;;;;;;;;;;;;;;;;;;;;;;;;;;

(defn kleene* [elements]
  (letfn [(expand [strings] (for [s strings e elements] (conj s e)))]
    (->>
      (lazy-seq (kleene* elements))
      expand
      (cons []))))

(defn library-of-babel []
  (let [ascii (->> (range 32 127) (map char))]
    (->> ascii
       kleene*
       (map (partial apply str)))))

(fact "We can construct all strings as a lazy sequence."
  (->> (library-of-babel) (take 5)) => ["" " " "!" "\"" "#"]
  (nth (library-of-babel) 364645) => "GEB")

(fact "Lexicons aren't very random."
  (randomness (take 10000 (library-of-babel))) => #(< % 1/100))

(comment
  (take 100000
     (letfn[(t[](cons[](for[x(lazy-seq(t))e(map char(range 32 65536))](conj x e))))](map #(apply str %)(take-while #(<(count %)141)(t))))))

;;;;;;;;;;;;;;;;
;;; Contact ;;;;
;;;;;;;;;;;;;;;;

(defn decompose [n]
  (let [[remainder quotient] ((juxt mod quot) n 10)]
    (if (zero? quotient)
      [remainder]
      (conj (decompose quotient) remainder))))

(defn champernowne-word
  ([from]
   (->> (range)
        (map (partial + from))
        (mapcat decompose)))
  ([]
   (champernowne-word 0)))

(fact "The Champernowne word is defined by concatenating the natural numbers base 10."
  (->> (champernowne-word) (take 16)) => [0 1 2 3 4 5 6 7 8 9 1 0 1 1 1 2])

;;;;;;;;;;;;
;;; Anti ;;;
;;;;;;;;;;;;

(defmethod live/play-note :default
  [{hertz :pitch seconds :duration}]
  (when hertz (geb/overchauffeur (midi->hz hertz) seconds)))

(defn copyright-infringement-song
  ([skip-to]
   (->>
     (champernowne-word skip-to)
     (coding/decode 3)
     (where :time (bpm 120))
     (where :duration (bpm 120))))
   ([] (copyright-infringement-song 0)))

(def blurred-lines 12450012001200311273127612731276127312761273127612731276127312761245001200121245001200120031127312761273127612731276127312761273127612731276124500120012124500120012003112731276127312761273127612731276127312761273127612450012001212450012001200311273127612731276127312761273127612731276127312761245001200121240001200120031126812711268127112681271126812711268127112681271124000120012124000120012003112681271126812711268127112681271126812711268127112400012001212400012001200311268127112681271126812711268127112681271126812711240001200121252004100411264125012621249126112471245)

(comment
  (live/play (copyright-infringement-song blurred-lines))
  (live/play (copyright-infringement-song)))

\end{verbatim}

\bibliographystyle{abbrvnat}

% The bibliography should be embedded for final submission.

\begin{thebibliography}{}
\softraggedright

\bibitem[Smith et~al.(2009)Smith, Jones]{smith02}
P. Q. Smith, and X. Y. Jones. ...reference text...

\end{thebibliography}

\end{document}

### 2016-04-02 paper.tex
Break the code up into sections.

@@
 
+\section{Air on the \\G String}
 \begin{verbatim}
-(ns kolmogorov-music.talk
-  (:require [clojure.repl :as repl]
-            [midje.sweet :refer :all :exclude [after]]
-            [overtone.live :refer :all :exclude [stop]]
-            [leipzig.melody :refer :all]
-            [leipzig.canon :as canon]
-            [leipzig.scale :as scale]
-            [leipzig.live :as live]
-            [leipzig.live :refer [stop]]
-            [leipzig.chord :as chord]
-            [leipzig.temperament :as temperament]
-            [kolmogorov-music.geb :as geb]
-            [kolmogorov-music.coding :as coding]))
-
-;;;;;;;;;;;;;;;;;;;;;;;;;;;;
-;;; Air on the \G String ;;;
-;;;;;;;;;;;;;;;;;;;;;;;;;;;;
-
 (comment (take 10000 (repeat (* 1000 1000 1000 1000) \G)))
@@
 
-;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;
-;;; Analysis by compression ;;;
-;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;;
+\end{verbatim}
 
+\section{Analysis by compression}
+
+\begin{verbatim}
 (def row-row
@@
 
-;;;;;;;;;;;;;;;;;;;;;;;;;;;;
-;;; The Library of Babel ;;;
-;;;;;;;;;;;;;;;;;;;;;;;;;;;;
+\end{verbatim}
+
+\section{The Library of Babel}
+\begin{verbatim}
 
@@
 
-;;;;;;;;;;;;;;;;
-;;; Contact ;;;;
-;;;;;;;;;;;;;;;;
+\end{verbatim}
+
+\section{Contact}
+\begin{verbatim}
 
@@
   (->> (champernowne-word) (take 16)) => [0 1 2 3 4 5 6 7 8 9 1 0 1 1 1 2])
+\end{verbatim}
 
-;;;;;;;;;;;;
-;;; Anti ;;;
-;;;;;;;;;;;;
+\section{Anti}
+\begin{verbatim}
 

### 2016-04-02 paper.tex
Add hyperref package for URLs.
Add a couple of bibliography items.
Fix the backslash in the G string reference.
Add Blurred Lines as a section.
Add an abstract.

@@
 % Based on the template for sigplanconf LaTeX Class by Paul C. Anagnostopoulos (paul@windfall.com)
-\documentclass[preprint]{sigplanconf}
+\documentclass[numbers]{sigplanconf}
 
 \usepackage{amsmath}
+\usepackage{hyperref}
 
@@
 
-\title{Algomusicology, ?, Profit}
+\title{Algomusicology, ???, Profit}
 %\subtitle{Subtitle Text, if any}
@@
 \begin{abstract}
-This is the text of the abstract.
+    In this paper I propose a novel method for converting algomusicology into profit. While my particular example
+    is slightly tongue-in-cheek, my serious point is that algorithmic composition can help us deconstruct and
+    disrupt traditional notions of musical authorship.
 \end{abstract}
@@
 
-\keywords
-keyword1, keyword2
+%\keywords
+%keyword1, keyword2
 
@@
 
-\section{Air on the \\G String}
+\section{Air on the {\textbackslash}G String}
 \begin{verbatim}
@@
 \section{Anti}
+
+\section{Blurred Lines}
 \begin{verbatim}
@@
 
-\bibliographystyle{abbrvnat}
+\bibliographystyle{plainnat}
 
@@
 
-\bibitem[Smith et~al.(2009)Smith, Jones]{smith02}
-P. Q. Smith, and X. Y. Jones. ...reference text...
+\bibitem{Overtone} Aaron, Sam and Rose, Jeff: Overtone (\url{http://overtone.github.io})
+\bibitem{Anti EP} Autechre: Anti EP (\url{https://en.wikipedia.org/wiki/Anti_EP})
 

### 2016-04-02 paper.tex
Add English to the code.

@@
 \section{Air on the {\textbackslash}G String}
+Very great quantities of data can exhibit very little complexity. Consider the following Clojure expression, which
+evaluates to a sequence of $10^{15}$ uppercase G characters:
+
 \begin{verbatim}
-(comment (take 10000 (repeat (* 1000 1000 1000 1000) \G)))
+(repeat (* 1000 1000 1000 1000 1000) \G)
+\end{verbatim}
+
+Though storing such a string would require roughly a petabyte of memory, representing it indirectly as a computation
+takes very little space at all. To put it in perspective, that's roughly the size all music recorded to date,
+described in less than a half a tweet \footnote{Based on the iTunes library featuring approximately 50 million songs
+of approximately 4 megabytes each, and assuming it represents approximately a fifth of all recorded music.}.
+
+We can use Clojure's macro facility to build a crude framework for comparing the size of descriptions and their
+resulting values. The following two definitions are identical, save that description-length is a macro and therefore
+operates on the unevaluated s-expression passed to it as an argument.
+
+\begin{verbatim}
+(defn result-length [expression]
+  (-> expression print-str count))
 
@@
 
-(defn result-length [expression]
-  (-> expression print-str count))
-
-(fact "The description-length is how long the string representation of the expression is."
-  (description-length (repeat 65 \G)) => 13)
-
-(fact "The result-length is how long the string representation of the evaluated result is."
+(fact "The result-length is how long the string
+       representation of the evaluated result is."
   (result-length (repeat 65 \G)) => 131)
 
+(fact "The description-length is how long the
+       string representation of the expression is."
+  (description-length (repeat 65 \G)) => 13)
+\end{verbatim}
+
+The randomness of a description can be measured by comparing the length of the textual description and the length
+of the resulting value.
+
+\begin{verbatim}
 (defmacro randomness [expression]
-  `(/ (description-length ~expression) (result-length ~expression)))
+  `(/ (description-length ~expression)
+      (result-length ~expression)))
 
-(fact "Kolmogorov randomness is the compression ratio between the description and the result."
-  (randomness (repeat 65 \G)) => 13/131
-  (randomness (->> 71 char repeat first)) => 26)
-
+(fact "Kolmogorov randomness is the compression
+       ratio between the description and the result."
+  (randomness (repeat 65 \G)) => 13/131)
 \end{verbatim}
@@
 \section{Analysis by compression}
+
+David Meredith has used Kolmogorov complexity to compare the quality of musical analyses. The theory goes that the
+more concise the algorithmic description of a piece, the better the musical model.
+
+Using this idea, we can show that composing "Row, row, row your boat" out of sequences of durations and pitches
+is a better description of the piece than the raw notes.
 
@@
        (where :pitch (comp scale/A scale/major))))
+\end{verbatim}
 
-(comment
-  (live/play row-row)
-  (live/jam (var row-row))
-)
+Using a little more macro magic, we can calculate the ratio between the above description and the literal notes
+of the song.
 
+\begin{verbatim}
 (defmacro definitionally [macro sym]
@@
 
-(fact "The definitionally macro lets us calculate on the definition of symbols."
+(fact "The definitionally macro lets us calculate on the
+       definition of symbols."
   (definitionally description-length row-row) => 281
@@
   (definitionally randomness row-row) => 281/2037)
-
 \end{verbatim}
@@
 \section{The Library of Babel}
+
+The Kleene star is the set of all possible substrings built from a set of elements.
+
 \begin{verbatim}
-
 (defn kleene* [elements]
-  (letfn [(expand [strings] (for [s strings e elements] (conj s e)))]
+  (letfn [(expand [strings]
+            (for [s strings e elements] (conj s e)))]
     (->>
@@
       (cons []))))
+\end{verbatim}
 
+We can use the Kleene star with an alphabet of the ASCII alphabet to construct all possible ASCII strings as a lazy
+sequence. This results in something very similar to the Library of Babel as imagined by Jorge Luis Borges. In this
+vast building of library, are all possible books of four hundred and ten pages in length.
+
+The difference is that our sequence has all possible strings of all finite lengths.
+
+\begin{verbatim}
 (defn library-of-babel []
@@
 
-(fact "We can construct all strings as a lazy sequence."
-  (->> (library-of-babel) (take 5)) => ["" " " "!" "\"" "#"]
-  (nth (library-of-babel) 364645) => "GEB")
-
-(fact "Lexicons aren't very random."
-  (randomness (take 10000 (library-of-babel))) => #(< % 1/100))
-
-(comment
-  (take 100000
-     (letfn[(t[](cons[](for[x(lazy-seq(t))e(map char(range 32 65536))](conj x e))))](map #(apply str %)(take-while #(<(count %)141)(t))))))
-
+(fact "We can construct all strings as a lazy
+       sequence."
+  (->> (library-of-babel) (take 5))
+    => ["" " " "!" "\"" "#"]
+  (nth (library-of-babel) 364645)
+    => "GEB")
 \end{verbatim}
 
+Lexicon's are interesting from a Kolmogorov complexity perspective, because they can be described concisely yet contain
+multitudes. Paradoxically, lexicons display the property that the whole is simpler than (almost all of) the parts. That is,
+the Kolmogorov complexity of all strings in our Library of Babel beyond a certain size are more complicated to describe
+than the Library as a whole.
+
+Borges appreciated this paradox. His anonymous narrator concludes that "On some shelf in some hexagon (men reasoned)
+there must exist a book which is the formula and perfect compendium of all the rest"?????. Any of the many books that contain
+our library-of-babel function match the narrator's description, though the books that also contain the rest of this paper
+must surely provide more helpful context.
+
 \section{Contact}
+
+The Champernowne word is a transcendental constant whose decimal expansion is the concatenation of the digits of the
+natural numbers.
+
 \begin{verbatim}
-
 (defn decompose [n]
@@
 
-(fact "The Champernowne word is defined by concatenating the natural numbers base 10."
-  (->> (champernowne-word) (take 16)) => [0 1 2 3 4 5 6 7 8 9 1 0 1 1 1 2])
+(fact "The Champernowne word is defined by concatenating the
+       natural numbers base 10."
+  (->> (champernowne-word) (take 16))
+    => [0 1 2 3 4 5 6 7 8 9 1 0 1 1 1 2])
 \end{verbatim}
@@
 \section{Blurred Lines}
+
+'Blurred Lines' is a pop song that was written by Pharrell Williams and Robin Thicke. In March 2015,
+they were found to have infringed on the copyright of the Marvin Gaye song 'Got to Give It Up'.
 \begin{verbatim}
-
-(defmethod live/play-note :default
-  [{hertz :pitch seconds :duration}]
-  (when hertz (geb/overchauffeur (midi->hz hertz) seconds)))
-
 (defn copyright-infringement-song
@@
 (def blurred-lines 12450012001200311273127612731276127312761273127612731276127312761245001200121245001200120031127312761273127612731276127312761273127612731276124500120012124500120012003112731276127312761273127612731276127312761273127612450012001212450012001200311273127612731276127312761273127612731276127312761245001200121240001200120031126812711268127112681271126812711268127112681271124000120012124000120012003112681271126812711268127112681271126812711268127112400012001212400012001200311268127112681271126812711268127112681271126812711240001200121252004100411264125012621249126112471245)
-
-(comment
-  (live/play (copyright-infringement-song blurred-lines))
-  (live/play (copyright-infringement-song)))
-
 \end{verbatim}

### 2016-04-02 paper.tex
Add introduction.

@@
 
-\title{Algomusicology, ???, Profit}
+\title{Algomusicology, ?, Profit}
 %\subtitle{Subtitle Text, if any}
@@
     In this paper I propose a novel method for converting algomusicology into profit. While my particular example
-    is slightly tongue-in-cheek, my serious point is that algorithmic composition can help us deconstruct and
-    disrupt traditional notions of musical authorship.
+    is tongue-in-cheek, my serious point is that algorithmic composition can help us deconstruct and disrupt
+    traditional notions of musical authorship.
 \end{abstract}
@@
 \section{Introduction}
+
+The Underpants Gnomes are renowned for their business plan:
+\begin{itemize}
+    \item Collect underpants
+    \item ?
+    \item Profit
+\end{itemize}
+
+Art critics, literary critics, Algomusicologists have a challenge in common with the Underpants Gnomes, we may have
+collected a vast amount of underpants/art/users, but how are we to turn that into profit? Less glibly, is algomusicology
+doomed to be a mere observer and explainer of musical practice, or might it become an active participant? Computer science is
+able to influence industry, though that might take longer than we'd like \footnote{Alonzo Church developed the
+lambda calculus in the 1930s. Java gained lambda expressions in 2015.}. Can algomusicology influence music?
+
+The examples in this paper are all written in Clojure, dialect of Lisp. I also rely on Leipzig, a small music theory
+library written in Clojure and Midje, for music theoretical functions, and Midje, a unit testing library, for assertions.
 

### 2016-04-02 paper.tex
Elaboration.

@@
 In this paper I propose a novel method for converting algomusicology into profit. While my particular example
-    is tongue-in-cheek, my serious point is that algorithmic composition can help us deconstruct and disrupt
+is tongue-in-cheek, it shows that algorithmic composition and analysis can help us deconstruct and disrupt
 traditional notions of musical authorship.
@@
 
-Art critics, literary critics, Algomusicologists have a challenge in common with the Underpants Gnomes, we may have
-collected a vast amount of underpants/art/users, but how are we to turn that into profit? Less glibly, is algomusicology
+Art critics, literary critics, algomusicologists and Twitter have a challenge in common with the Underpants Gnomes - we may have
+collected a considerable quantity of underpants/art/users, but how are we to turn that into profit? Less glibly, is algomusicology
 doomed to be a mere observer and explainer of musical practice, or might it become an active participant? Computer science is
 able to influence industry, though that might take longer than we'd like \footnote{Alonzo Church developed the
-lambda calculus in the 1930s. Java gained lambda expressions in 2015.}. Can algomusicology influence music?
+lambda calculus in the 1930s. Java gained lambda expressions in 2015.}. Can algomusicology influence music?\footnote{This paper
+appears to be the first reference to algomusicology. I believe the term, which is a portmanteau of algorave and musicology,
+has a self-evident definition.}
 
-The examples in this paper are all written in Clojure, dialect of Lisp. I also rely on Leipzig, a small music theory
-library written in Clojure and Midje, for music theoretical functions, and Midje, a unit testing library, for assertions.
+This paper will argue that it can. It will do so by citing examples of existing art works that are algorithmic in nature, and
+also by using algomusicological concepts to create a work that challenges our present conception of musical authorship and
+copyright.
+
+The examples in this paper are all written in Clojure, dialect of Lisp. I also rely on Leipzig, a music theory library written
+in Clojure and Midje, a unit testing library, for its fact notation.
 
@@
 Though storing such a string would require roughly a petabyte of memory, representing it indirectly as a computation
-takes very little space at all. To put it in perspective, that's roughly the size all music recorded to date,
-described in less than a half a tweet \footnote{Based on the iTunes library featuring approximately 50 million songs
-of approximately 4 megabytes each, and assuming it represents approximately a fifth of all recorded music.}.
+takes very little space at all. To put it in perspective, that's roughly the size all music ever recorded to date,
+described in less than a half a tweet\footnote{Based on the iTunes library featuring approximately 50 million songs
+of approximately 4 megabytes each, and assuming it represents approximately a fifth of all recorded music. Tweets are
+restricted to 140 characters.}.
 
@@
 
-(fact "The result-length is how long the string
-       representation of the evaluated result is."
-  (result-length (repeat 65 \G)) => 131)
-
-(fact "The description-length is how long the
-       string representation of the expression is."
+(fact
+  (result-length (repeat 65 \G)) => 131
   (description-length (repeat 65 \G)) => 13)
@@
 The randomness of a description can be measured by comparing the length of the textual description and the length
-of the resulting value.
+of the resulting value. If there is no way to describe a value more concisely than the value itself, we say that it is
+random.
 
@@
 
-(fact "Kolmogorov randomness is the compression
-       ratio between the description and the result."
+(fact
   (randomness (repeat 65 \G)) => 13/131)
@@
 \begin{verbatim}
-(defmacro definitionally [macro sym]
+(defmacro definitional [macro sym]
   (let [value (-> sym repl/source-fn read-string last)]
@@
 
-(fact "The definitionally macro lets us calculate on the
-       definition of symbols."
-  (definitionally description-length row-row) => 281
-  (definitionally result-length row-row) => 2037
-  (definitionally randomness row-row) => 281/2037)
+(fact
+  (definitional description-length row-row) => 281
+  (definitional result-length row-row) => 2037
+  (definitional randomness row-row) => 281/2037)
 \end{verbatim}
@@
 
-(fact "We can construct all strings as a lazy
-       sequence."
-  (->> (library-of-babel) (take 5))
-    => ["" " " "!" "\"" "#"]
-  (nth (library-of-babel) 364645)
-    => "GEB")
+(fact
+  (->> (library-of-babel) (take 3)) => ["" " " "!"]
+  (nth (library-of-babel) 364645) => "GEB")
 \end{verbatim}
@@
 
-Borges appreciated this paradox. His anonymous narrator concludes that "On some shelf in some hexagon (men reasoned)
+Borges appreciated this paradox. His anonymous narrator reports that on "some shelf in some hexagon (men reasoned)
 there must exist a book which is the formula and perfect compendium of all the rest"?????. Any of the many books that contain
@@
 
-The Champernowne word is a transcendental constant whose decimal expansion is the concatenation of the digits of the
-natural numbers.
+In Carl Sagan's novel 'Contact', he imagines that a message to humanity is encoded in the digits of pi. If we design an
+appropriate encoding scheme, we could do a similar thing and treat the digits of pi as music. However, we would encounter
+a similar problem to Borges' librarians - we suspect that every sequence of data we could possibly want is in there
+somewhere, but we don't know where to look.
+
+Fortunately, there are other transcendental numbers that are more predictable. The Champernowne word is a constant whose
+decimal expansion is the concatenation of the digits of the natural numbers.
 
 \begin{verbatim}
-(defn decompose [n]
+(defn decompose-into-digits [n]
   (let [[remainder quotient] ((juxt mod quot) n 10)]
@@
       [remainder]
-      (conj (decompose quotient) remainder))))
+      (conj (decompose-into-digits quotient) remainder))))
 
@@
         (map (partial + from))
-        (mapcat decompose)))
+        (mapcat decompose-into-digits)))
   ([]
@@
 
-(fact "The Champernowne word is defined by concatenating the
-       natural numbers base 10."
+(fact
   (->> (champernowne-word) (take 16))
@@
 
+\section{Conclusion}
+
 \bibliographystyle{plainnat}

### 2016-04-02 paper.tex
Use explanatory-power instead of randomness (as explanatory-power is relative to a particular description and randommness isn't really).

@@
 
-The randomness of a description can be measured by comparing the length of the textual description and the length
-of the resulting value. If there is no way to describe a value more concisely than the value itself, we say that it is
-random.
+The explanatory power of a description can be measured by comparing the length of the textual description and the length
+of the resulting value. Explanatory power is the reciprocal of the compression ratio, where representing a value by an
+expression is viewed as a compression strategy.
+
+If there is no way to describe a value more concisely than the value itself, we say that it is random. An explanatory
+power of one or less is no explanation at all.
 
 \begin{verbatim}
-(defmacro randomness [expression]
-  `(/ (description-length ~expression)
-      (result-length ~expression)))
+(defmacro explanatory-power [expression]
+  `(/ (result-length ~expression)
+      (description-length ~expression)))
 
 (fact
-  (randomness (repeat 65 \G)) => 13/131)
+  (explanatory-power (repeat 65 \G)) => 131/13)
 \end{verbatim}
@@
 Using a little more macro magic, we can calculate the ratio between the above description and the literal notes
-of the song.
+of the song. The definitional macro allows us to use the symbol row-row in our fact notation, rather than having to
+paste in the entire expression.
 
@@
   (definitional result-length row-row) => 2037
-  (definitional randomness row-row) => 281/2037)
+  (definitional explanatory-power row-row) => 2037/281)
 \end{verbatim}

### 2016-04-02 paper.tex
Format function names in monospace.

@@
 
-The Underpants Gnomes are renowned for their business plan:
-\begin{itemize}
+The South Park Underpants Gnomes are renowned for their business plan:
+\begin{enumerate}
     \item Collect underpants
@@
     \item Profit
-\end{itemize}
+\end{enumerate}
 
-Art critics, literary critics, algomusicologists and Twitter have a challenge in common with the Underpants Gnomes - we may have
-collected a considerable quantity of underpants/art/users, but how are we to turn that into profit? Less glibly, is algomusicology
-doomed to be a mere observer and explainer of musical practice, or might it become an active participant? Computer science is
-able to influence industry, though that might take longer than we'd like \footnote{Alonzo Church developed the
-lambda calculus in the 1930s. Java gained lambda expressions in 2015.}. Can algomusicology influence music?\footnote{This paper
-appears to be the first reference to algomusicology. I believe the term, which is a portmanteau of algorave and musicology,
-has a self-evident definition.}
+A common interpretation of the Gnomes' business is as a satire on Silicon Valley startups. Art critics, literary critics,
+algomusicologists and start-uppers have a challenge in common with the Underpants Gnomes
+- we may have collected a considerable quantity of underpants/art/users, but how are we to turn that into profit?
+
+Less glibly, is algomusicology doomed to be a mere observer and explainer of musical practice, or might it become an
+active participant? Computer science is able to influence industry, though that might take longer than we'd like.
+\footnote{Alonzo Church developed the lambda calculus in the 1930s. Java gained lambda expressions in 2015.} Can
+algomusicology influence music?\footnote{This paper appears to be the first reference to algomusicology. I believe the term,
+which is a portmanteau of algorave and musicology, has a self-evident definition.}
 
@@
 
-The examples in this paper are all written in Clojure, dialect of Lisp. I also rely on Leipzig, a music theory library written
-in Clojure and Midje, a unit testing library, for its fact notation.
+The examples in this paper are all written in Clojure, a dialect of Lisp. I also rely on Leipzig, a music theory library,
+and Midje, a unit testing library.\footnote{Midje allows us to write a unit test as (fact expression => result),
+which asserts that expression evaluates to result.}
 
@@
 Though storing such a string would require roughly a petabyte of memory, representing it indirectly as a computation
-takes very little space at all. To put it in perspective, that's roughly the size all music ever recorded to date,
+takes very little space at all. To put it in perspective, that's roughly the size all music ever recorded,
 described in less than a half a tweet\footnote{Based on the iTunes library featuring approximately 50 million songs
@@
 We can use Clojure's macro facility to build a crude framework for comparing the size of descriptions and their
-resulting values. The following two definitions are identical, save that description-length is a macro and therefore
-operates on the unevaluated s-expression passed to it as an argument.
+resulting values. The following two definitions are identical, save that \verb|description-length| is a macro and therefore
+operates on the unevaluated expression that is passed to it.
 
@@
 
-If there is no way to describe a value more concisely than the value itself, we say that it is random. An explanatory
-power of one or less is no explanation at all.
+If there is no way to describe a value more concisely than the value itself, we say that it is random. In other words an
+explanatory power of one or less is no explanation at all.
 
@@
 Using a little more macro magic, we can calculate the ratio between the above description and the literal notes
-of the song. The definitional macro allows us to use the symbol row-row in our fact notation, rather than having to
-paste in the entire expression.
+of the song. The \verb|definitional| macro allows us to use the symbol \verb|row-row| in our fact notation, rather than
+having to paste in the entire expression.
 

### 2016-04-02 paper.tex
Fill out the rest of the argument.

@@
   (-> expression print-str count))
+\end{verbatim}
 
+Here is an example of using these definitions to calculate the description and result length of a short sequence of Gs.
+
+\begin{verbatim}
 (fact
@@
 The explanatory power of a description can be measured by comparing the length of the textual description and the length
-of the resulting value. Explanatory power is the reciprocal of the compression ratio, where representing a value by an
+of the resulting value. Explanatory power is equivalent to the compression power, where representing a value by an
 expression is viewed as a compression strategy.
@@
 If there is no way to describe a value more concisely than the value itself, we say that it is random. In other words an
-explanatory power of one or less is no explanation at all.
+explanatory power of one or less is no explanation at all. In compression terms, there is no possible space saving
+to be gained by representing this value by an expression.
 
@@
       (description-length ~expression)))
+\end{verbatim}
 
+The explanatory power of our expression for producing 65 Gs is high. A repetitive string of identical characters is
+highly redundant, highly compressible and hence able to be described concisely. The explanatory power of this way of
+representing the string of Gs this way is over 10.
+
+\begin{verbatim}
 (fact
@@
 \end{verbatim}
+
+There are many expressions that evaluate to the same value, so there are likely to be different expressions of varying
+explanatory power. The Kolmogorov complexity is defined as the length of the briefest possible description. This is not,
+in general, computable, so it's not possible to determine whether we have obtained the best possible explanation for a
+piece of data.
 
@@
 
-Lexicon's are interesting from a Kolmogorov complexity perspective, because they can be described concisely yet contain
+Lexicons are interesting from a Kolmogorov complexity perspective, because they can be described concisely yet contain
 multitudes. Paradoxically, lexicons display the property that the whole is simpler than (almost all of) the parts. That is,
 the Kolmogorov complexity of all strings in our Library of Babel beyond a certain size are more complicated to describe
-than the Library as a whole.
+than the Library taken as a whole.
 
@@
 there must exist a book which is the formula and perfect compendium of all the rest"?????. Any of the many books that contain
-our library-of-babel function match the narrator's description, though the books that also contain the rest of this paper
+our \verb|library-of-babel| function match the narrator's description, though the books that also contain the rest of this paper
 must surely provide more helpful context.
@@
 (defn champernowne-word
-  ([from]
+  [skip-to]
   (->> (range)
-        (map (partial + from))
+       (map (partial + skip-to))
        (mapcat decompose-into-digits)))
-  ([]
-   (champernowne-word 0)))
 
 (fact
-  (->> (champernowne-word) (take 16))
+  (->> (champernowne-word 0) (take 16))
     => [0 1 2 3 4 5 6 7 8 9 1 0 1 1 1 2])
@@
 
+Here we generate the Champernowne word in the way that it is normally done. We start at zero, and decompose the digits of
+every subsequent natural number. However, we could just as easily start at any other natural number, which is demonstrated
+by the \verb|skip-to| argument. This is a useful property, because it lets us jump straight to any part of the constant
+without having to generate all the previous digits.
+
 \section{Anti}
+
+A notorious example. The British government of the time wished to discourage rave culture, so it passed legislation that banned
+music with "repetitive beats"?????. Autechre responded with a track in which every bar features a unique beat?????.
 
@@
 they were found to have infringed on the copyright of the Marvin Gaye song 'Got to Give It Up'.
+
+As a response to this situation, I decided to compose a track that would infringe on the copyright of both songs. The following
+piece decodes the Champernowne word into music.
+
 \begin{verbatim}
 (defn copyright-infringement-song
-  ([skip-to]
+  [skip-to]
   (->>
@@
     (coding/decode 3)
-     (where :time (bpm 120))
-     (where :duration (bpm 120))))
-   ([] (copyright-infringement-song 0)))
-
-(def blurred-lines 12450012001200311273127612731276127312761273127612731276127312761245001200121245001200120031127312761273127612731276127312761273127612731276124500120012124500120012003112731276127312761273127612731276127312761273127612450012001212450012001200311273127612731276127312761273127612731276127312761245001200121240001200120031126812711268127112681271126812711268127112681271124000120012124000120012003112681271126812711268127112681271126812711268127112400012001212400012001200311268127112681271126812711268127112681271126812711240001200121252004100411264125012621249126112471245)
+    (tempo (bpm 120))))
 \end{verbatim}
 
+As the Champernowne word's digits are predictable, I am able to skip ahead to any part of the song I choose. Here
+is the value of \verb|skip-to| that results in a passable version of 'Blurred Lines'.\footnote{The encoding scheme is chosen
+to be reversible, which allowed me to determine where in the Champernowne word 'Blurred Lines' would occur. Full details are in the accompanying code.}
+
+\begin{verbatim}
+(def gaye-williams-thicke-constant
+  12450012001200311273127612731276127312761273127612731...
+  27612731276124500120012124500120012003112731276127312...
+  76127312761273127612731276127312761245001200121245001...
+  20012003112731276127312761273127612731276127312761273...
+  12761245001200121245001200120031127312761273127612731...
+  27612731276127312761273127612450012001212400012001200...
+  31126812711268127112681271126812711268127112681271124...
+  00012001212400012001200311268127112681271126812711268...
+  12711268127112681271124000120012124000120012003112681...
+  27112681271126812711268127112681271126812711240001200...
+  121252004100411264125012621249126112471245)
+\end{verbatim}
+
+There is nothing in the description of the \verb|copyright-infringement-song| that is in any way related to 'Blurred Lines'.
+It is simply a straightforward musical rendering of a well-known mathematical constant derived from the decimal counting
+system.
+
+What's more, every other song is also somewhere in there.
+
+Here we finally come to the profit generation strategy - copyright litigation. As the \verb|copyright-infringement-song| is
+a universal piece of music, any work published subsequent to it infringes on its copyright.\footnote{I am not a lawyer. Do not rely on my legal advice.}
+
 \section{Conclusion}
+
+\begin{enumerate}
+    \item Algomusicology
+    \item Copyright litigation
+    \item Profit!
+\end{enumerate}
 

### 2016-04-02 paper.tex
Talk more about lexicons.

@@
 
-Lexicons are interesting from a Kolmogorov complexity perspective, because they can be described concisely yet contain
-multitudes. Paradoxically, lexicons display the property that the whole is simpler than (almost all of) the parts. That is,
-the Kolmogorov complexity of all strings in our Library of Babel beyond a certain size are more complicated to describe
+If we take the Kleene star of a particular alphabet, order the results countably, and then concatenate them, we get
+a disjunctive sequence or lexicon. A lexicon has the property that every finite string is a substring.
+
+The result of the Kleene star are interesting from a Kolmogorov complexity perspective, because they can be described
+concisely yet contain multitudes. Paradoxically, it displays the property that the whole is simpler than (almost all of)
+the parts. That is, the Kolmogorov complexity of one string in our Library of Babel is more complicated to describe
 than the Library taken as a whole.
@@
 
+If pi does have every possible of digits within its decimal expansion, then it's a disjunctive
+sequence or lexicon. But we don't know for sure.
+
 Fortunately, there are other transcendental numbers that are more predictable. The Champernowne word is a constant whose
-decimal expansion is the concatenation of the digits of the natural numbers.
+decimal expansion is the concatenation of the digits of the natural numbers. The Champernowne word is definitively a lexicon,
+which can be concluded by observing that it eventually contains any natural number. Any sequence of digits corresponds to
+a natural number, so the word must contain all sequences of digits.
+
+Of course, the sequence of digits may occur earlier too - the string "34" first occurs when the natural numbers three and
+four are serialised, well before the natural number 34 is.
 

### 2016-04-02 paper.tex
Use the briefer anonymous fn syntax to avoid overspilling.

@@
          (phrase (repeat 12 1/3)
-                 (mapcat (partial repeat 3) [7 4 2 0])))
+                 (mapcat #(repeat 3 %) [7 4 2 0])))
        (then

### 2016-04-02 paper.tex
Fine tune.

@@
 Though storing such a string would require roughly a petabyte of memory, representing it indirectly as a computation
-takes very little space at all. To put it in perspective, that's roughly the size all music ever recorded,
+takes very little space at all. That's roughly the size all music ever recorded,
 described in less than a half a tweet\footnote{Based on the iTunes library featuring approximately 50 million songs
@@
 highly redundant, highly compressible and hence able to be described concisely. The explanatory power of this way of
-representing the string of Gs this way is over 10.
+representing the string of Gs this way is just over 10, because the description is about a tenth of the length of the
+value itself.
 
@@
 There are many expressions that evaluate to the same value, so there are likely to be different expressions of varying
-explanatory power. The Kolmogorov complexity is defined as the length of the briefest possible description. This is not,
-in general, computable, so it's not possible to determine whether we have obtained the best possible explanation for a
-piece of data.
+explanatory power for the same value. The Kolmogorov complexity is defined as the length of the briefest possible description.
+This is not, in general, computable, so it's not possible to determine whether we have obtained the best possible explanation
+for an arbitrary piece of data.
 
@@
 
-The Kleene star is the set of all possible substrings built from a set of elements.
+The Kleene star is the set of all possible strings built from a set of elements.
 
@@
 
-We can use the Kleene star with an alphabet of the ASCII alphabet to construct all possible ASCII strings as a lazy
-sequence. This results in something very similar to the Library of Babel as imagined by Jorge Luis Borges. In this
-vast building of library, are all possible books of four hundred and ten pages in length.
+We can use this construction with an ASCII alphabet to obtain all possible ASCII strings as a lazy
+sequence. This results in something very similar to the Library of Babel as imagined by Jorge Luis Borges. In his
+vast fictional library, thousands of hexagonal rooms house all possible books of four hundred and ten pages.
 
@@
        kleene*
-       (map (partial apply str)))))
+       (map #(apply str %)))))
 
@@
 
-If we take the Kleene star of a particular alphabet, order the results countably, and then concatenate them, we get
+If we take the Kleene star of a particular alphabet, order the results and then concatenate them, we get
 a disjunctive sequence or lexicon. A lexicon has the property that every finite string is a substring.
@@
 Borges appreciated this paradox. His anonymous narrator reports that on "some shelf in some hexagon (men reasoned)
-there must exist a book which is the formula and perfect compendium of all the rest"?????. Any of the many books that contain
-our \verb|library-of-babel| function match the narrator's description, though the books that also contain the rest of this paper
-must surely provide more helpful context.
+there must exist a book which is the formula and perfect compendium of all the rest"?????. In other words, that one book
+epitomises the complexity of the entire library.
+
+Any of the many books that contain our \verb|library-of-babel| function match the narrator's description,
+though the books that also contain the rest of this paper must surely provide more helpful context.
 
@@
 If pi does have every possible of digits within its decimal expansion, then it's a disjunctive
-sequence or lexicon. But we don't know for sure.
+sequence or lexicon. But we don't know for sure. No one has been able to prove that pi is either disjunctive or not disjunctive.
 
@@
 decimal expansion is the concatenation of the digits of the natural numbers. The Champernowne word is definitively a lexicon,
-which can be concluded by observing that it eventually contains any natural number. Any sequence of digits corresponds to
+which can be concluded by observing that it eventually contains every natural number. Every sequence of digits corresponds to
 a natural number, so the word must contain all sequences of digits.
@@
 Of course, the sequence of digits may occur earlier too - the string "34" first occurs when the natural numbers three and
-four are serialised, well before the natural number 34 is.
+four are encountered, well before the natural number 34 is.
 
@@
   (->> (range)
-       (map (partial + skip-to))
+       (map #(+ skip-to %))
        (mapcat decompose-into-digits)))
@@
 
-What's more, every other song is also somewhere in there.
+What's more, every other song is also somewhere in there. Past, present and future.
 
 Here we finally come to the profit generation strategy - copyright litigation. As the \verb|copyright-infringement-song| is
-a universal piece of music, any work published subsequent to it infringes on its copyright.\footnote{I am not a lawyer. Do not rely on my legal advice.}
+a universal piece of music, any work published subsequent to it infringes on its copyright.\footnote{I am not a lawyer.
+Do not rely on my legal advice.} In order to convert our algomusicological understanding into profit, we simply have to sue the composers
+of every marginally successful musical work from now until they change the law.
 

### 2016-04-02 paper.tex
A listing of a set is an enumeration.

@@
 
-The Kleene star is the set of all possible strings built from a set of elements.
+The Kleene star is the set of all possible strings built from a set of elements. Here is a function that takes a set of
+elements and produces an enumeration of the Kleene star of the set as a lazy sequence.
 
@@
 
-We can use this construction with an ASCII alphabet to obtain all possible ASCII strings as a lazy
-sequence. This results in something very similar to the Library of Babel as imagined by Jorge Luis Borges. In his
+We can use this construction with an ASCII alphabet to obtain all possible ASCII strings.
+This results in something very similar to the Library of Babel as imagined by Jorge Luis Borges. In his
 vast fictional library, thousands of hexagonal rooms house all possible books of four hundred and ten pages.

### 2016-04-03 paper.tex
General draft, including updating the copyright notice.

@@
 
-\title{Algomusicology, ???, Profit}
+\publicationrights{author-pays}
+
+\title{Algomusicology, ????, Profit}
 %\subtitle{Subtitle Text, if any}
@@
 
-A common interpretation of the Gnomes' business is as a satire on Silicon Valley startups. Art critics, literary critics,
-algomusicologists and start-uppers have a challenge in common with the Underpants Gnomes
-- we may have collected a considerable quantity of underpants/art/users, but how are we to turn that into profit?
+A common interpretation of the Gnomes' business is as a satire on Silicon Valley startups.
+Algomusicologists and starter-uppers have a challenge in common with the Underpants Gnomes
+- we may have collected and analysed a considerable quantity of underpants/music/users, but how are we to turn that into profit?
 
 Less glibly, is algomusicology doomed to be a mere observer and explainer of musical practice, or might it become an
-active participant? Computer science is able to influence industry, though that might take longer than we'd like.
-\footnote{Alonzo Church developed the lambda calculus in the 1930s. Java gained lambda expressions in 2015.} Can
-algomusicology influence music?\footnote{This paper appears to be the first reference to algomusicology. I believe the term,
+active participant in the conversation? Computer science is able to influence the software industry, though that might take longer
+than we'd like. \footnote{Alonzo Church developed the lambda calculus in the 1930s. Java gained lambda expressions in 2015.}
+Can algomusicology influence music?\footnote{This paper appears to be the first reference to algomusicology. I believe the term,
 which is a portmanteau of algorave and musicology, has a self-evident definition.}
@@
 The examples in this paper are all written in Clojure, a dialect of Lisp. I also rely on Leipzig, a music theory library,
+\footnote{Leipzig provides ways of describing notes in terms of higher order concepts like chords and scales.}
 and Midje, a unit testing library.\footnote{Midje allows us to write a unit test as (fact expression => result),
@@
 resulting values. The following two definitions are identical, save that \verb|description-length| is a macro and therefore
-operates on the unevaluated expression that is passed to it.
+operates on the unevaluated expression.
 
@@
 The explanatory power of a description can be measured by comparing the length of the textual description and the length
-of the resulting value. Explanatory power is equivalent to the compression power, where representing a value by an
+of the resulting value. Explanatory power is equivalent to compression power, where representing a value via an
 expression is viewed as a compression strategy.
 
-If there is no way to describe a value more concisely than the value itself, we say that it is random. In other words an
+If there is no way to describe a value more concisely than the value itself, we say that it is random. In other words, an
 explanatory power of one or less is no explanation at all. In compression terms, there is no possible space saving
-to be gained by representing this value by an expression.
+by representing this value by an expression.
 
@@
 
-The explanatory power of our expression for producing 65 Gs is high. A repetitive string of identical characters is
-highly redundant, highly compressible and hence able to be described concisely. The explanatory power of this way of
+The explanatory power of our description of 65 Gs is high. A repetitive string of identical characters is
+highly redundant, highly compressible and hence amenable to concise description. The explanatory power of this way of
 representing the string of Gs this way is just over 10, because the description is about a tenth of the length of the
@@
 (def row-row
-  "A simple melody built from durations and pitches."
                 ; Row, row, row  your boat,
@@
                  [  0    0    0    1    2])
-       (then
-                ; Gent-ly   down the  stream,
+
+       (then    ; Gent-ly   down the  stream,
          (phrase [2/3  1/3  2/3  1/3  6/3]
                  [  2    1    2    3    4]))
+
        (then    ; Merrily, merrily, merrily, merrily,
@@
                  (mapcat #(repeat 3 %) [7 4 2 0])))
-       (then
-                ; Life is   but  a    dream!
+
+       (then    ; Life is   but  a    dream!
          (phrase [2/3  1/3  2/3  1/3  6/3]
                  [  4    3    2    1    0]))
-       (canon/canon (canon/simple 4))
-       (where :pitch (comp scale/A scale/major))))
+
+       (canon (simple 4))
+       (where :pitch (comp A major))))
 \end{verbatim}
 
-Using a little more macro magic, we can calculate the ratio between the above description and the literal notes
-of the song. The \verb|definitional| macro allows us to use the symbol \verb|row-row| in our fact notation, rather than
+We can calculate the ratio between the literal notes of the song and the above description.
+The \verb|definitional| macro allows us to use the symbol \verb|row-row| in our fact notation, rather than
 having to paste in the entire expression.
@@
 
-If we take the Kleene star of a particular alphabet, order the results and then concatenate them, we get
+If we enumerate and then concatenate the Kleene star of a particular alphabet, it produces
 a disjunctive sequence or lexicon. A lexicon has the property that every finite string is a substring.
@@
 
-If pi does have every possible of digits within its decimal expansion, then it's a disjunctive
-sequence or lexicon. But we don't know for sure. No one has been able to prove that pi is either disjunctive or not disjunctive.
+If pi's decimal expansion does have every possible combination of digits, then it's what is known as a disjunctive
+sequence or lexicon. But we don't know for sure. No one has been able to prove it either way.
 
-Fortunately, there are other transcendental numbers that are more predictable. The Champernowne word is a constant whose
-decimal expansion is the concatenation of the digits of the natural numbers. The Champernowne word is definitively a lexicon,
-which can be concluded by observing that it eventually contains every natural number. Every sequence of digits corresponds to
-a natural number, so the word must contain all sequences of digits.
+Fortunately, there are other transcendental numbers that are more predictable. The Champernowne constant has a
+decimal expansion that is the concatenation of the digits of the natural numbers. To refer to the sequence of digits
+in its decimal expansion we can simply refer to the Champernowne word.
 
-Of course, the sequence of digits may occur earlier too - the string "34" first occurs when the natural numbers three and
-four are encountered, well before the natural number 34 is.
+Here we construct the Champernowne word by decomposing each natural number into its constituent digits and concatenating
+the results together.
 
@@
 
-Here we generate the Champernowne word in the way that it is normally done. We start at zero, and decompose the digits of
+It is easily seen to be a lexicon for the decimal digits, because:
+\begin{enumerate}
+    \item By definition, the Champernowne word includes every natural number.
+    \item Every sequence of digits corresponds to a natural number.
+    \item Therefore, the Champernowne word contains all possible sequences of digits.
+\end{enumerate}
+Of course, a sequence of digits may occur earlier than its natural number - the sequence "34" first occurs when numbers three and
+four are encountered, well in advance of the natural number 34.
+
+In the above example we generate the word starting from zero, and decompose the digits of
 every subsequent natural number. However, we could just as easily start at any other natural number, which is demonstrated
-by the \verb|skip-to| argument. This is a useful property, because it lets us jump straight to any part of the constant
+by the \verb|skip-to| parameter. This is a useful property, because it lets us jump straight to any part of the constant
 without having to generate all the previous digits.
@@
 As a response to this situation, I decided to compose a track that would infringe on the copyright of both songs. The following
-piece decodes the Champernowne word into music.
+piece decodes the Champernowne word into music of three parts.
 
@@
 Do not rely on my legal advice.} In order to convert our algomusicological understanding into profit, we simply have to sue the composers
-of every marginally successful musical work from now until they change the law.
+of every marginally successful musical work from now until they fix the law.
 
@@
 \end{enumerate}
+
+\acks
+
+Thank you to the StrangeLoop conference of 2015, which accepted the talk 'Kolmogorov Music' from which this paper derives.
 

### 2016-04-03 paper.tex
Expand on Autechre.

@@
 The Kleene star is the set of all possible strings built from a set of elements. Here is a function that takes a set of
-elements and produces an enumeration of the Kleene star of the set as a lazy sequence.
+elements and enumerates the Kleene star of that set as a lazy sequence.
 
@@
 
-\section{Anti}
+\section{Flutter}
 
-A notorious example. The British government of the time wished to discourage rave culture, so it passed legislation that banned
-music with "repetitive beats"?????. Autechre responded with a track in which every bar features a unique beat?????.
+The Criminal Justice and Public Order Act 1994 was an attempt by the UK Government to curb rave culture. The musicological
+dilemma encountered by the government of the day was how to define raves. They settled on prohibiting gatherings where
+"a succession of repetitive beats" were played.
+
+The duo Autechre responded with the Anti EP, whose third track 'Flutter', was designed to protest the legislation. Band member
+Sean Booth explained that they "made as many different bars as we could on the drum machine, then strung them all together."
+In other words, as every bar features a unique beat, 'Flutter' does not match the government's algomusicological description
+of "repetitive beats".
+
+Autechre appreciated the practical difficulties of negotiating the subtleties of complexity theory at 3am in a field,
+so they advised DJs to "have a lawyer and a musicologist present at all times to confirm the non repetitive nature of the
+music in the event of police harassment."
+
+Both legislators and artists are clearly taking algomusicological positions. The government attempted to construct the set
+of all rave musics using a complexity characterisation. Autechre responded with what amounts to a diagonal argument, demonstrating
+the inadequacy of the original claim.
 
@@
 
-'Blurred Lines' is a pop song that was written by Pharrell Williams and Robin Thicke. In March 2015,
+'Blurred Lines' is a 2013 pop song written by Pharrell Williams and Robin Thicke. In March 2015,
 they were found to have infringed on the copyright of the Marvin Gaye song 'Got to Give It Up'.
 
+Such judgements are perilous from a musicological point of view, as they are often based on a jury's intuition as to
+the similarity between songs and not, for example, on a conditional Kolmogorov complexity analysis of the distance between
+the two compositions.
+
 As a response to this situation, I decided to compose a track that would infringe on the copyright of both songs. The following
-piece decodes the Champernowne word into music of three parts.
+piece decodes the Champernowne word into music.
 
@@
 
-What's more, every other song is also somewhere in there. Past, present and future.
+What's more, every other song is also somewhere in there. Past, present and future compositions already exist somewhere in
+the depths of this infinite piece.
 

### 2016-04-03 paper.tex
Fill out references.

@@
 
-The South Park Underpants Gnomes are renowned for their business plan:
+The South Park Underpants Gnomes\cite{Gnomes} are renowned for their business plan:
 \begin{enumerate}
@@
 
-The examples in this paper are all written in Clojure, a dialect of Lisp. I also rely on Leipzig, a music theory library,
+The examples in this paper are all written in Clojure, a dialect of Lisp. I also rely on Leipzig\cite{Leipzig},
+a music theory library,
 \footnote{Leipzig provides ways of describing notes in terms of higher order concepts like chords and scales.}
-and Midje, a unit testing library.\footnote{Midje allows us to write a unit test as (fact expression => result),
+and Midje\cite{Midje}, a unit testing library.\footnote{Midje allows us to write a unit test as (fact expression => result),
 which asserts that expression evaluates to result.}
 
-\section{Air on the {\textbackslash}G String}
+\section{Air on the {\textbackslash}G String\cite{Air on the G String}}
 Very great quantities of data can exhibit very little complexity. Consider the following Clojure expression, which
@@
 restricted to 140 characters.}.
+
+The insight that the inherent complexity of data can be measured by the length of the computer program needed to express it
+originates with Andrey Kolmogorov\cite{On Tables of Random Numbers}. The Kolmogorov complexity of a piece of data is defined
+as the length of the shortest program that evaluates to it.
 
@@
 
-David Meredith has used Kolmogorov complexity to compare the quality of musical analyses. The theory goes that the
+David Meredith has used Kolmogorov complexity to compare the quality of musical analyses\cite{Analysis by Compression}.
+The theory goes that the
 more concise the algorithmic description of a piece, the better the musical model.
@@
 We can use this construction with an ASCII alphabet to obtain all possible ASCII strings.
-This results in something very similar to the Library of Babel as imagined by Jorge Luis Borges. In his
+This results in something very similar to the Library of Babel as imagined by Jorge Luis Borges\cite{The Library of Babel}. In his
 vast fictional library, thousands of hexagonal rooms house all possible books of four hundred and ten pages.
@@
 
-In Carl Sagan's novel 'Contact', he imagines that a message to humanity is encoded in the digits of pi. If we design an
-appropriate encoding scheme, we could do a similar thing and treat the digits of pi as music. However, we would encounter
-a similar problem to Borges' librarians - we suspect that every sequence of data we could possibly want is in there
-somewhere, but we don't know where to look.
+In Carl Sagan's novel 'Contact'\cite{Contact}, he imagines that a message to humanity is encoded in the digits of pi.
+If we design an appropriate encoding scheme, we could do a similar thing and treat the digits of pi as music. However,
+we would encounter a similar problem to Borges' librarians - we suspect that every sequence of data we could possibly want
+is in there somewhere, but we don't know where to look.
 
@@
 dilemma encountered by the government of the day was how to define raves. They settled on prohibiting gatherings where
-"a succession of repetitive beats" were played.
+"a succession of repetitive beats" were played\cite{Joseph Gallivan on pop}.
 
-The duo Autechre responded with the Anti EP, whose third track 'Flutter', was designed to protest the legislation. Band member
+The duo Autechre responded with the Anti EP\cite{Anti EP}, whose third track 'Flutter', was designed to protest the legislation.
+Band member
 Sean Booth explained that they "made as many different bars as we could on the drum machine, then strung them all together."
+\cite{Joseph Gallivan on pop}
 In other words, as every bar features a unique beat, 'Flutter' does not match the government's algomusicological description
@@
 so they advised DJs to "have a lawyer and a musicologist present at all times to confirm the non repetitive nature of the
-music in the event of police harassment."
+music in the event of police harassment."\cite{Joseph Gallivan on pop}
 
@@
 
-'Blurred Lines' is a 2013 pop song written by Pharrell Williams and Robin Thicke. In March 2015,
-they were found to have infringed on the copyright of the Marvin Gaye song 'Got to Give It Up'.
+'Blurred Lines' is a 2013 pop song written by Pharrell Williams and Robin Thicke\cite{Blurred Lines}. In March 2015,
+they were found to have infringed on the copyright of the Marvin Gaye song 'Got to Give It Up'\cite{Got to Give It Up}.
 
@@
 \bibitem{Anti EP} Autechre: Anti EP (\url{https://en.wikipedia.org/wiki/Anti_EP})
+\bibitem{Air on the G String} Bach, Johann Sebastian: Air on the G String
+\bibitem{The Library of Babel} Borges, Jorge Luis
+\bibitem{Gnomes} Brady, Pam, Parker, Trey and Stone, Matt. Episode 17, season 2 of South Park
+\bibitem{Got to Give It Up} Got to Give It Up: Gaye, Marvin
+\bibitem{Leipzig} Ford, Chris: Leipzig
+\bibitem{Joseph Gallivan on pop} Gallivan, Joseph: Joseph Gallivan on pop (\url{http://www.independent.co.uk/life-style/jospeh-gallivan-on-pop-1414727.html})
+\bibitem{On Tables of Random Numbers}  Kolmogorov, Andrey: On Tables of Random Numbers
+\bibitem{Midje} Marick, Brian: Midje
+\bibitem{Analysis by Compression} Meredith, David: Analysis by Compression
+\bibitem{Contact} Sagan, Carl: Contact
+\bibitem{Blurred Lines} Williams, Pharrel and Thicke, Robin: Blurred Lines
 

### 2016-04-03 paper.tex
Fix some more references.

@@
 
-The examples in this paper are all written in Clojure, a dialect of Lisp. I also rely on Leipzig\cite{Leipzig},
-a music theory library,
-\footnote{Leipzig provides ways of describing notes in terms of higher order concepts like chords and scales.}
-and Midje\cite{Midje}, a unit testing library.\footnote{Midje allows us to write a unit test as (fact expression => result),
-which asserts that expression evaluates to result.}
+The examples in this paper are all written in Clojure\cite{Clojure}, a dialect of Lisp. I also rely on Leipzig\cite{Leipzig},
+a music theory library, and Midje\cite{Midje}, a unit testing library.
 
@@
 Here is an example of using these definitions to calculate the description and result length of a short sequence of Gs.
+The \verb|fact| notation is due to Midje, which allows us to write \verb|(fact expression => result)|,
+which asserts that \verb|expression| evaluates to \verb|result|.
 
@@
 Using this idea, we can show that composing "Row, row, row your boat" out of sequences of durations and pitches
-is a better description of the piece than the raw notes.
+is a better description of the piece than the raw notes. The music functions e.g. \verb|phrase| are due to Leipzig,
+and emit a time series data structure representing the resulting notes. \verb|;| indicates a comment in Clojure.
 
@@
 Borges appreciated this paradox. His anonymous narrator reports that on "some shelf in some hexagon (men reasoned)
-there must exist a book which is the formula and perfect compendium of all the rest"?????. In other words, that one book
+there must exist a book which is the formula and perfect compendium of all the rest". In other words, that one book
 epitomises the complexity of the entire library.
@@
 'Blurred Lines' is a 2013 pop song written by Pharrell Williams and Robin Thicke\cite{Blurred Lines}. In March 2015,
-they were found to have infringed on the copyright of the Marvin Gaye song 'Got to Give It Up'\cite{Got to Give It Up}.
+they were found to have infringed on the copyright of the Marvin Gaye song 'Got to Give It Up'\cite{Got to Give It Up}
+\cite{USA Today}.
 
@@
 
+Thank you also to Sam Aaron and Jeff Rose for giving the world Overtone\cite{Overtone}, the audio programming environment
+that made this paper possible.
+
 \bibliographystyle{plainnat}
@@
 \bibitem{Overtone} Aaron, Sam and Rose, Jeff: Overtone (\url{http://overtone.github.io})
-\bibitem{Anti EP} Autechre: Anti EP (\url{https://en.wikipedia.org/wiki/Anti_EP})
-\bibitem{Air on the G String} Bach, Johann Sebastian: Air on the G String
-\bibitem{The Library of Babel} Borges, Jorge Luis
+\bibitem{Anti EP} Autechre: Anti EP
+\bibitem{Air on the G String} Wilhelmj, August arranging Bach, Johann Sebastian: Air on the G String
+\bibitem{The Library of Babel} Borges, Jorge Luis: The Library of Babel
 \bibitem{Gnomes} Brady, Pam, Parker, Trey and Stone, Matt. Episode 17, season 2 of South Park
@@
 \bibitem{Joseph Gallivan on pop} Gallivan, Joseph: Joseph Gallivan on pop (\url{http://www.independent.co.uk/life-style/jospeh-gallivan-on-pop-1414727.html})
+\bibitem{Clojure} Hickey, Rich: Clojure
 \bibitem{On Tables of Random Numbers}  Kolmogorov, Andrey: On Tables of Random Numbers
@@
 \bibitem{Analysis by Compression} Meredith, David: Analysis by Compression
+\bibitem{USA Today} Oldenburg, Ann: 'Blurred Lines' jury finds for Marvin Gaye (\url{http://www.usatoday.com/story/life/music/2015/03/10/blurred-lines-trial-verdict/24492431/})
 \bibitem{Contact} Sagan, Carl: Contact

### 2016-04-03 paper.tex
Fix a particularly egrarious overspill.
Set document to preprint.
Cite Champernowne.

@@
 % Based on the template for sigplanconf LaTeX Class by Paul C. Anagnostopoulos (paul@windfall.com)
-\documentclass[numbers]{sigplanconf}
+\documentclass[numbers, preprint]{sigplanconf}
 
@@
 \publicationrights{author-pays}
+
+\titlebanner{Submission for FARM 2016}
 
@@
 
-Fortunately, there are other transcendental numbers that are more predictable. The Champernowne constant has a
+Fortunately, there are other transcendental numbers that are more predictable. The Champernowne constant was discovered
+by David Champernowne as an undergraduate\cite{The construction of decimals normal in the scale of ten}. It has a
 decimal expansion that is the concatenation of the digits of the natural numbers. To refer to the sequence of digits
@@
       [remainder]
-      (conj (decompose-into-digits quotient) remainder))))
+      (conj
+        (decompose-into-digits quotient)
+        remainder))))
 
@@
 \bibitem{The Library of Babel} Borges, Jorge Luis: The Library of Babel
+\bibitem{The construction of decimals normal in the scale of ten} Champernowne, David: The construction of decimals normal in the scale of ten
 \bibitem{Gnomes} Brady, Pam, Parker, Trey and Stone, Matt. Episode 17, season 2 of South Park

### 2016-04-03 paper.tex
Add understated irony.

@@
 
-Autechre appreciated the practical difficulties of negotiating the subtleties of complexity theory at 3am in a field,
+Autechre appreciated the practical difficulties of negotiating the subtleties of complexity theory at 3am in a noisy field,
 so they advised DJs to "have a lawyer and a musicologist present at all times to confirm the non repetitive nature of the

### 2016-04-17 paper.tex
Incorporate @txus's feedback.

@@
 David Meredith has used Kolmogorov complexity to compare the quality of musical analyses\cite{Analysis by Compression}.
-The theory goes that the
-more concise the algorithmic description of a piece, the better the musical model.
+He starts by assuming that musical analysis aims to produce "best possible explanation for musical works". If that's the case,
+how might we compare two different analyses of the same piece?
+
+Meredith's answer is that by representing an analysis of a piece of music as a computer program, we can use Kolmogov complexity
+to objectively measure the quality of the explanation it provides. A short program must necessarily capture a lot of the structure
+of a piece, because summarising a piece's structure is the only way to achieve compression. A longer program is a worse explanation,
+because it has missed opportunities to exploit the structure of the piece.
+
+Representing the notes of a piece as code is straightforward, as a series of notes can, to a first approximation,
+be generated from a sequence of durations and a sequence of pitches. The following example uses Leipzig's \verb|phrase| function,
+and produces a sequence of time/pitch/duration tuples.
+
+\begin{verbatim}
+  (phrase [3/3  3/3  2/3  1/3  3/3]
+          [  0    0    0    1    2])
+\end{verbatim}
+
+Individual phrases can be combined together to form larger pieces. Here are two equivalent ways of playing the above melody twice.
+
+\begin{verbatim}
+  (->>
+    (phrase [3/3  3/3  2/3  1/3  3/3]
+            [  0    0    0    1    2])
+    (then
+      (phrase [3/3  3/3  2/3  1/3  3/3]
+              [  0    0    0    1    2])))
+
+  (->>
+    (phrase [3/3  3/3  2/3  1/3  3/3]
+            [  0    0    0    1    2])
+    (times 2))
+\end{verbatim}
+
+The latter way is considerably shorter. It also demonstrates a greater understanding of the piece. The notes are exactly
+repeated twice, so writing them out again longhand is a waste. The first way of writing the notes misses this opportunity to
+summarise and is therefore a worse explanation.
 
 Using this idea, we can show that composing "Row, row, row your boat" out of sequences of durations and pitches
-is a better description of the piece than the raw notes. The music functions e.g. \verb|phrase| are due to Leipzig,
-and emit a time series data structure representing the resulting notes. \verb|;| indicates a comment in Clojure.
+is a better description of the piece than the raw notes. \verb|;| indicates a comment in Clojure.
 
@@
 
+The particularly significant compression in this way of writing "Row, row, row your boat" is the line \verb|(canon (simple 4))|.
+A canon is when an initial melody (often known as the dux) is accompanied by a transformation of itself (often known as the comes).
+In "Row, row, row your boat", the comes is a copy of the dux that is delayed by four beats, a structure known as a simple canon.
+
+Here is the definition of \verb|canon|:
+
+\begin{verbatim}
+(defn canon [f notes]
+  (->> (f notes) (with notes)))
+\end{verbatim}
+
+In a canon, every note has two lives. Firstly, it is played straight. Secondly, it is played again in a modified form according
+to the canon's \verb|f|. By understanding this, we can almost halve the length of the program we need to
+produce the piece.
+
+The more concise the algorithmic description of a piece, the better the musical model.
+
 \section{The Library of Babel}
 
-The Kleene star is the set of all possible strings built from a set of elements. Here is a function that takes a set of
-elements and enumerates the Kleene star of that set as a lazy sequence.
+The Kleene star is the set of all possible strings that can be built from a set of elements. Here is a function that takes a set
+of elements and enumerates the Kleene star a lazy sequence. It works by taking the strings generated thus far, appending each
+element to each string and then repeating the process. This results in an infinite lazy sequence of strings of ever increasing
+length, starting from the empty string.
 
@@
 
-If we enumerate and then concatenate the Kleene star of a particular alphabet, it produces
-a disjunctive sequence or lexicon. A lexicon has the property that every finite string is a substring.
+If we enumerate the Kleene star of a particular alphabet, we get a sequence of all its possible strings.
+If we concatenate them all together into one long string, it produces what is known as a disjunctive sequence or lexicon.
+A lexicon has the property that every finite string is a substring.
 
-The result of the Kleene star are interesting from a Kolmogorov complexity perspective, because they can be described
+The results of the Kleene star are interesting from a Kolmogorov complexity perspective, because they can be described
 concisely yet contain multitudes. Paradoxically, it displays the property that the whole is simpler than (almost all of)

### 2016-04-17 paper.tex
Incorporate some of @namin's feedback.
Incorporate @nadamin's footnote protip.

@@
 active participant in the conversation? Computer science is able to influence the software industry, though that might take longer
-than we'd like. \footnote{Alonzo Church developed the lambda calculus in the 1930s. Java gained lambda expressions in 2015.}
-Can algomusicology influence music?\footnote{This paper appears to be the first reference to algomusicology. I believe the term,
+than we'd like.~\footnote{Alonzo Church developed the lambda calculus in the 1930s. Java gained lambda expressions in 2015.}
+Can algomusicology influence music?~\footnote{This paper appears to be the first reference to algomusicology. I believe the term,
 which is a portmanteau of algorave and musicology, has a self-evident definition.}
@@
 takes very little space at all. That's roughly the size all music ever recorded,
-described in less than a half a tweet\footnote{Based on the iTunes library featuring approximately 50 million songs
+described in less than a half a tweet.~\footnote{Based on the iTunes library featuring approximately 50 million songs
 of approximately 4 megabytes each, and assuming it represents approximately a fifth of all recorded music. Tweets are
-restricted to 140 characters.}.
+restricted to 140 characters.}
 
@@
 If we concatenate them all together into one long string, it produces what is known as a disjunctive sequence or lexicon.
-A lexicon has the property that every finite string is a substring.
+A lexicon contains every finite string as a substring.
 
@@
 As the Champernowne word's digits are predictable, I am able to skip ahead to any part of the song I choose. Here
-is the value of \verb|skip-to| that results in a passable version of 'Blurred Lines'.\footnote{The encoding scheme is chosen
+is the value of \verb|skip-to| that results in a passable version of 'Blurred Lines'.~\footnote{The encoding scheme is chosen
 to be reversible, which allowed me to determine where in the Champernowne word 'Blurred Lines' would occur. Full details are in the accompanying code.}
@@
 Here we finally come to the profit generation strategy - copyright litigation. As the \verb|copyright-infringement-song| is
-a universal piece of music, any work published subsequent to it infringes on its copyright.\footnote{I am not a lawyer.
+a universal piece of music, any work published subsequent to it infringes on its copyright.~\footnote{I am not a lawyer.
 Do not rely on my legal advice.} In order to convert our algomusicological understanding into profit, we simply have to sue the composers

### 2016-04-17 paper.tex
Incorporate @namin's citation protip.
Light drafting.

@@
 originates with Andrey Kolmogorov\cite{On Tables of Random Numbers}. The Kolmogorov complexity of a piece of data is defined
-as the length of the shortest program that evaluates to it.
+as the length of the shortest program that evaluates to it. The greater the structural regularity, the more opportunities
+to express the data using a short expression.
 
@@
 of a piece, because summarising a piece's structure is the only way to achieve compression. A longer program is a worse explanation,
-because it has missed opportunities to exploit the structure of the piece.
+because it has missed opportunities to exploit structural regularities in the piece.
 
@@
 summarise and is therefore a worse explanation.
+
+One might imagine that a maintainer of this musical code would refactor the former expression into the latter. Viewed this way,
+refactoring away repetition can be seen as improving the explanatory power of the code.
 
@@
 In a canon, every note has two lives. Firstly, it is played straight. Secondly, it is played again in a modified form according
-to the canon's \verb|f|. By understanding this, we can almost halve the length of the program we need to
-produce the piece.
+to the canon's \verb|f|. By understanding this, we can almost halve the length of the program we need to produce the piece.
 
@@
 
-We can use this construction with an ASCII alphabet to obtain all possible ASCII strings.
+We can use this construction with an ASCII alphabet to obtain all possible ASCII strings. We might just as easily have
+used the letters 'G', 'A', 'T' and 'C' to generate every possible DNA sequence.
+
 This results in something very similar to the Library of Babel as imagined by Jorge Luis Borges\cite{The Library of Babel}. In his
-vast fictional library, thousands of hexagonal rooms house all possible books of four hundred and ten pages.
+vast fictional library, thousands of hexagonal rooms house all possible books of four hundred and ten pages. Melancholic
+librarians spend their entire lives toiling in its maddiningly symetrical depths.
 
-The difference is that our sequence has all possible strings of all finite lengths.
+Some books exhibit apparent sense, most exhibit none. The narrator describes one that is "a mere labyrinth of letters,
+but the next-to-last page says \textit|Oh time thy pyramids|."
+
+Unlike Borges's library, our strings are not limited to four hundred and ten pages. Because of this limit, the Library of Babel
+must either be finite, or have identical copies of the same book. Our list is an infinite sequence of all possible strings of
+all finite lengths.
 
@@
 If we concatenate them all together into one long string, it produces what is known as a disjunctive sequence or lexicon.
-A lexicon contains every finite string as a substring.
+A lexicon contains every finite string as a substring. It's called a lexicon because it says everything that is possible
+to say with that alphabet.
 
 The results of the Kleene star are interesting from a Kolmogorov complexity perspective, because they can be described
-concisely yet contain multitudes. Paradoxically, it displays the property that the whole is simpler than (almost all of)
-the parts. That is, the Kolmogorov complexity of one string in our Library of Babel is more complicated to describe
-than the Library taken as a whole.
+concisely yet contain multitudes. Paradoxically, the whole is simpler than (almost all of) the parts.
+That is, the Kolmogorov complexity of one string in our Library of Babel is more complicated to describe than the Library
+taken as a whole.
 
@@
 there must exist a book which is the formula and perfect compendium of all the rest". In other words, that one book
-epitomises the complexity of the entire library.
+epitomises the complexity of the entire library, though it is part of the library.
 
@@
 
-If pi's decimal expansion does have every possible combination of digits, then it's what is known as a disjunctive
-sequence or lexicon. But we don't know for sure. No one has been able to prove it either way.
+If pi's decimal expansion does have every possible combination of digits, then it's a lexicon for the decimal digits.
+But we don't know for sure. No one has been able to prove it either way.
 
@@
 'Blurred Lines' is a 2013 pop song written by Pharrell Williams and Robin Thicke\cite{Blurred Lines}. In March 2015,
-they were found to have infringed on the copyright of the Marvin Gaye song 'Got to Give It Up'\cite{Got to Give It Up}
-\cite{USA Today}.
+they were found to have infringed on the copyright of the Marvin Gaye song
+'Got to Give It Up'\cite{Got to Give It Up, USA Today}.
 

### 2016-04-17 paper.tex
Add an appendix on the encoding scheme.

@@
 is the value of \verb|skip-to| that results in a passable version of 'Blurred Lines'.~\footnote{The encoding scheme is chosen
-to be reversible, which allowed me to determine where in the Champernowne word 'Blurred Lines' would occur. Full details are in the accompanying code.}
+to be reversible, which allowed me to determine where in the Champernowne word 'Blurred Lines' would occur. Full details are in the appendix and the accompanying code.}
 
@@
 (def gaye-williams-thicke-constant
-  12450012001200311273127612731276127312761273127612731...
-  27612731276124500120012124500120012003112731276127312...
-  76127312761273127612731276127312761245001200121245001...
-  20012003112731276127312761273127612731276127312761273...
-  12761245001200121245001200120031127312761273127612731...
-  27612731276127312761273127612450012001212400012001200...
-  31126812711268127112681271126812711268127112681271124...
-  00012001212400012001200311268127112681271126812711268...
-  12711268127112681271124000120012124000120012003112681...
-  27112681271126812711268127112681271126812711240001200...
-  121252004100411264125012621249126112471245)
+  124500120012003112731276127312761273127...
+  612731276127312761273127612450012001212...
+  450012001200311273127612731276127312761...
+  273127612731276127312761245001200121245...
+  001200120031127312761273127612731276127...
+  312761273127612731276124500120012124500...
+  120012003112731276127312761273127612731...
+  276127312761273127612450012001212400012...
+  001200311268127112681271126812711268127...
+  112681271126812711240001200121240001200...
+  120031126812711268127112681271126812711...
+  268127112681271124000120012124000120012...
+  003112681271126812711268127112681271126...
+  812711268127112400012001212520041004112...
+  64125012621249126112471245)
 \end{verbatim}
@@
 \end{enumerate}
+
+\appendix
+\section{Encoding the Champernowne Constant}
+
+It would not have been practical to discover the Gaye-Williams-Thicke constant by brute force. Playing through the song at normal
+speed would have seen the expansion of the sun into a red giant interrupt the search before it made much progress.
+
+Instead, I devised an encoding between the natural numbers and a piece of music. This allowed me to start with the music, encode
+it and therefore discover the constant. Playing the Champernowne Constant as music is the reverse process.
+
+The encoding is relatively simple, each four digit word in the natural number is turned into a note, two digits for duration and
+two digits for pitch. The two digits for duration are interpreted as a fraction, and the two digits for pitch as a midi code.
+
+\begin{verbatim}
+(fact
+  (->> (leipzig/phrase [2/3 1/3] [0 4]) encode)
+    => 23001304)
+\end{verbatim}
+
+When there are multiple parts, they are multiplexed, based on which part is furthest behind. It would not be sufficient to
+simply alternate between decoding a note of each part, as notes are not of uniform length. For example, in a two part piece
+with a rapid melody and a slow, ostinato bass, the melody part of the encoding would slip further and further behind as
+we alternately encoded one note from each part.
+
+\begin{verbatim}
+(fact
+  (->> (phrase [1 1 1 1] [0 1 2 3])
+       (with (phrase [2 2] [4 5]))
+       encode)
+    => 210411001101210511021103)
+\end{verbatim}
+
+Rests are encoded with zeros where duration normally is, leaving the other two digits for duration.
+This is convenient because a zero duration is otherwise meaningless.
+
+\begin{verbatim}
+(fact
+  (->> (phrase [1 1 1 1] [0 nil 2 nil]) encode)
+    => 1100001111020011)
+\end{verbatim}
+
+For the Gayte-Williams-Thicke constant. I wrote a version of 'Blurred Lines' with three parts and used a three part encoding.
 

### 2016-04-17 paper.tex
Add conclusion.

@@
 
+On one level, the puzzle posed by the title of this paper has a straightforward solution:
 \begin{enumerate}
@@
 \end{enumerate}
+
+More seriously, this paper attempts to show that algomusicology can meaningfully shed light on how music works. Also, as in
+the case of the \verb|copyright-infringement-song|, complexity theory can contribute ideas that are artistically interesting.
+In other words, algomusicology can contribute to musical practice, not just explain it.
+
+As an artform, music is an ideal subject for complexity analysis. Other media can also engage with complexity theory, but
+few are as tractable to complexity theory's techniques. Sagan and Borges may have written fiction that explores the implications
+of algorithmic creation, but it would be difficult to analyse 'Contact' and 'The Library of Babel' through Kolmogorov's lens.
 

### 2016-05-22 paper.tex
Proofread.

@@
 explanatory power of one or less is no explanation at all. In compression terms, there is no possible space saving
-by representing this value by an expression.
+by representing this value indirectly.
+
+The difficulty inherent in this definition is that we have no way of knowing if we have tried the most efficient way of
+computing a value or not. There are many ways to compute the same result. Some will be concise. These offer great
+explanatory power. Others will be verbose. These offer less explanatory power.
+
+Kolmogorov complexity is therefore uncomputable. Once we have found an expression that produces a value we can establish
+an upper bound for its Kolmogorov complexity, but we are unable to prove that we have found the most concise way to
+represent it.
+
+Fortunately, our inability to determine the complexity of a particular result does not prevent us from measuring the
+explanatory power of a particular description. Better descriptions may exist, but we need not worry about them.
+
+Here is a Clojure macro that calculates the explantory power of an expression as the ratio between the length of its
+result and the length of the expression itself.
 
@@
 
-The explanatory power of our description of 65 Gs is high. A repetitive string of identical characters is
+The explanatory power of our description of 65 Gs is great. A repetitive string of identical characters is
 highly redundant, highly compressible and hence amenable to concise description. The explanatory power of this way of
@@
 
-There are many expressions that evaluate to the same value, so there are likely to be different expressions of varying
-explanatory power for the same value. The Kolmogorov complexity is defined as the length of the briefest possible description.
-This is not, in general, computable, so it's not possible to determine whether we have obtained the best possible explanation
-for an arbitrary piece of data.
+There may be an even more concise way to represent our G string. If so, its Kolmogorov complexity may be even lower than
+131/13. However, we know for certain that 131/13 is an upper bound for the complexity of that string.
 
@@
 
-Representing the notes of a piece as code is straightforward, as a series of notes can, to a first approximation,
-be generated from a sequence of durations and a sequence of pitches. The following example uses Leipzig's \verb|phrase| function,
-and produces a sequence of time/pitch/duration tuples.
+Describing the notes of a musical work as code is straightforward, as notes can be represented by simple data structures like
+sequences of time/pitch tuples. Selecting which encoding scheme to use is less straightforward, because the choice of primitives
+can affect the complexity score. Ultimately, the choice of music theory library is difficult, somewhat subjective and
+will not be answered here.
+
+This paper uses Leipzig to provide its music theory primitives. Leipzig allows programmers to describe melodies as a sequence
+of durations and a sequence of pitches. The following example uses Leipzig's \verb|phrase| function to produces a sequence of
+time/pitch/duration tuples.
 
@@
 If we concatenate them all together into one long string, it produces what is known as a disjunctive sequence or lexicon.
-A lexicon contains every finite string as a substring. It's called a lexicon because it says everything that is possible
+A lexicon contains every finite string as a substring. It is called a lexicon because it says everything that is possible
 to say with that alphabet.
@@
 The results of the Kleene star are interesting from a Kolmogorov complexity perspective, because they can be described
-concisely yet contain multitudes. Paradoxically, the whole is simpler than (almost all of) the parts.
+concisely yet contain multitudes. Paradoxically, the whole can be simpler than the parts.
 That is, the Kolmogorov complexity of one string in our Library of Babel is more complicated to describe than the Library

### 2016-05-22 paper.tex
Fix single quotes.

@@
 We can use this construction with an ASCII alphabet to obtain all possible ASCII strings. We might just as easily have
-used the letters 'G', 'A', 'T' and 'C' to generate every possible DNA sequence.
+used the letters `G', `A', `T' and `C' to generate every possible DNA sequence.
 
@@
 
-In Carl Sagan's novel 'Contact'\cite{Contact}, he imagines that a message to humanity is encoded in the digits of pi.
+In Carl Sagan's novel `Contact'\cite{Contact}, he imagines that a message to humanity is encoded in the digits of pi.
 If we design an appropriate encoding scheme, we could do a similar thing and treat the digits of pi as music. However,
@@
 
-The duo Autechre responded with the Anti EP\cite{Anti EP}, whose third track 'Flutter', was designed to protest the legislation.
+The duo Autechre responded with the Anti EP\cite{Anti EP}, whose third track `Flutter', was designed to protest the legislation.
 Band member
@@
 \cite{Joseph Gallivan on pop}
-In other words, as every bar features a unique beat, 'Flutter' does not match the government's algomusicological description
+In other words, as every bar features a unique beat, `Flutter' does not match the government's algomusicological description
 of "repetitive beats".
@@
 
-'Blurred Lines' is a 2013 pop song written by Pharrell Williams and Robin Thicke\cite{Blurred Lines}. In March 2015,
+`Blurred Lines' is a 2013 pop song written by Pharrell Williams and Robin Thicke\cite{Blurred Lines}. In March 2015,
 they were found to have infringed on the copyright of the Marvin Gaye song
-'Got to Give It Up'\cite{Got to Give It Up, USA Today}.
+`Got to Give It Up'\cite{Got to Give It Up, USA Today}.
 
@@
 As the Champernowne word's digits are predictable, I am able to skip ahead to any part of the song I choose. Here
-is the value of \verb|skip-to| that results in a passable version of 'Blurred Lines'.~\footnote{The encoding scheme is chosen
-to be reversible, which allowed me to determine where in the Champernowne word 'Blurred Lines' would occur. Full details are in the appendix and the accompanying code.}
+is the value of \verb|skip-to| that results in a passable version of `Blurred Lines'.~\footnote{The encoding scheme is chosen
+to be reversible, which allowed me to determine where in the Champernowne word `Blurred Lines' would occur. Full details are in the appendix and the accompanying code.}
 
@@
 
-There is nothing in the description of the \verb|copyright-infringement-song| that is in any way related to 'Blurred Lines'.
+There is nothing in the description of the \verb|copyright-infringement-song| that is in any way related to `Blurred Lines'.
 It is simply a straightforward musical rendering of a well-known mathematical constant derived from the decimal counting

### 2016-05-22 paper.tex
Fix double quotes.

@@
 David Meredith has used Kolmogorov complexity to compare the quality of musical analyses\cite{Analysis by Compression}.
-He starts by assuming that musical analysis aims to produce "best possible explanation for musical works". If that's the case,
+He starts by assuming that musical analysis aims to produce ``best possible explanation for musical works". If that's the case,
 how might we compare two different analyses of the same piece?
@@
 
-Using this idea, we can show that composing "Row, row, row your boat" out of sequences of durations and pitches
+Using this idea, we can show that composing ``Row, row, row your boat" out of sequences of durations and pitches
 is a better description of the piece than the raw notes. \verb|;| indicates a comment in Clojure.
@@
 
-The particularly significant compression in this way of writing "Row, row, row your boat" is the line \verb|(canon (simple 4))|.
+The particularly significant compression in this way of writing ``Row, row, row your boat" is the line \verb|(canon (simple 4))|.
 A canon is when an initial melody (often known as the dux) is accompanied by a transformation of itself (often known as the comes).
-In "Row, row, row your boat", the comes is a copy of the dux that is delayed by four beats, a structure known as a simple canon.
+In ``Row, row, row your boat", the comes is a copy of the dux that is delayed by four beats, a structure known as a simple canon.
 
@@
 
-Some books exhibit apparent sense, most exhibit none. The narrator describes one that is "a mere labyrinth of letters,
+Some books exhibit apparent sense, most exhibit none. The narrator describes one that is ``a mere labyrinth of letters,
 but the next-to-last page says \textit|Oh time thy pyramids|."
@@
 
-Borges appreciated this paradox. His anonymous narrator reports that on "some shelf in some hexagon (men reasoned)
+Borges appreciated this paradox. His anonymous narrator reports that on ``some shelf in some hexagon (men reasoned)
 there must exist a book which is the formula and perfect compendium of all the rest". In other words, that one book
@@
 \end{enumerate}
-Of course, a sequence of digits may occur earlier than its natural number - the sequence "34" first occurs when numbers three and
+Of course, a sequence of digits may occur earlier than its natural number - the sequence ``34" first occurs when numbers three and
 four are encountered, well in advance of the natural number 34.
@@
 dilemma encountered by the government of the day was how to define raves. They settled on prohibiting gatherings where
-"a succession of repetitive beats" were played\cite{Joseph Gallivan on pop}.
+``a succession of repetitive beats" were played\cite{Joseph Gallivan on pop}.
 
@@
 Band member
-Sean Booth explained that they "made as many different bars as we could on the drum machine, then strung them all together."
+Sean Booth explained that they ``made as many different bars as we could on the drum machine, then strung them all together."
 \cite{Joseph Gallivan on pop}
 In other words, as every bar features a unique beat, `Flutter' does not match the government's algomusicological description
-of "repetitive beats".
+of ``repetitive beats".
 
 Autechre appreciated the practical difficulties of negotiating the subtleties of complexity theory at 3am in a noisy field,
-so they advised DJs to "have a lawyer and a musicologist present at all times to confirm the non repetitive nature of the
+so they advised DJs to ``have a lawyer and a musicologist present at all times to confirm the non repetitive nature of the
 music in the event of police harassment."\cite{Joseph Gallivan on pop}

### 2016-05-29 paper.tex
Tie the different parts together more explicitly.

@@
 
-This paper will argue that it can. It will do so by citing examples of existing art works that are algorithmic in nature, and
-also by using algomusicological concepts to create a work that challenges our present conception of musical authorship and
-copyright.
+This paper will argue that it can. It will do so by reviewing existing art works that are algorithmic in nature, and
+also by using algomusicological concepts to create a new work that challenges our present conception of musical authorship and
+copyright. As befits its subject matter, this paper will incorporate conventions and style from literary essays and musicology
+papers.
 
@@
 
+Music is widely regarded to have mathematical properties, but literature also contains examples of works where artists have engaged
+with algorithmic and information theoretical concepts. One striking case is the Library of Babel as imagined by Jorge Luis
+Borges\cite{The Library of Babel}. We will examine the story in a moment, but first we must define the mathematical concept
+that it revolves around - the Kleene star.
+
 The Kleene star is the set of all possible strings that can be built from a set of elements. Here is a function that takes a set
@@
 
-This results in something very similar to the Library of Babel as imagined by Jorge Luis Borges\cite{The Library of Babel}. In his
-vast fictional library, thousands of hexagonal rooms house all possible books of four hundred and ten pages. Melancholic
-librarians spend their entire lives toiling in its maddiningly symetrical depths.
+This results in something very similar to Borges' Library of Babel. In this vast fictional library, thousands of hexagonal
+rooms house all possible books of four hundred and ten pages. Melancholic librarians spend their entire lives toiling in its
+maddiningly symetrical depths.
 
@@
 there must exist a book which is the formula and perfect compendium of all the rest". In other words, that one book
-epitomises the complexity of the entire library, though it is part of the library.
+epitomises the complexity of the entire library, though it is part of the library. Any of the many books that contain our
+\verb|library-of-babel| function match the narrator's description, though the books that also contain the rest of this paper
+must surely provide more helpful context.
 
-Any of the many books that contain our \verb|library-of-babel| function match the narrator's description,
-though the books that also contain the rest of this paper must surely provide more helpful context.
+Through his Library of Babel, Borges is playing with our notions of invention versus discovery. Mathematicians and computer
+scientists struggle with whether they are the inventors of new theories or discoverers. Philip Wadler, for example,
+argues that the lambda calculus is such a fundamental concept that it deserves to be considered a universal concept that
+was discovered\cite{Propositions as Types}. By positing a library where any work may be found if you know where to look, Borges
+suggests that even literary authorship could be considered a search problem and therefore a matter of discovery rather than
+creation.
 
@@
 
-In Carl Sagan's novel `Contact'\cite{Contact}, he imagines that a message to humanity is encoded in the digits of pi.
-If we design an appropriate encoding scheme, we could do a similar thing and treat the digits of pi as music. However,
+In Carl Sagan's novel `Contact'\cite{Contact}, he takes the concept of discovering meaning in naturally occurring sources of
+information even further than Borges. Firstly, Sagan imagines that SETI detects a transmission consisting of a series of prime
+numbers from the the Vega star system. This prompts an exploration of how to distinguish between a signal created by an
+intelligence and one arising from natural symmetry.
+
+Later a message to humanity is discovered encoded in the digits of pi, placed there by beings who are able to manipulate the
+structure of the universe itself. This development questions the dichotomy between invented and discovered information altogether,
+by imagining a mathematical quantity as a medium for meaningful communication.
+
+If we design an appropriate encoding scheme, we could do a similar thing and interpret the digits of pi as music. However,
 we would encounter a similar problem to Borges' librarians - we suspect that every sequence of data we could possibly want
@@
 
-The Criminal Justice and Public Order Act 1994 was an attempt by the UK Government to curb rave culture. The musicological
-dilemma encountered by the government of the day was how to define raves. They settled on prohibiting gatherings where
-``a succession of repetitive beats" were played\cite{Joseph Gallivan on pop}.
+Complexity and information theory have been used to speculate on grand questions like the place of humanity in the universe,
+but they have also been used by artists to comment on specific social issues. The Criminal Justice and Public Order Act 1994
+was an attempt by the UK Government to curb rave culture. The musicological dilemma encountered by the government of the day
+was how to define raves. They settled on prohibiting gatherings where ``a succession of repetitive beats" were
+played\cite{Joseph Gallivan on pop}.
 
@@
 \section{Blurred Lines}
+
+We will now take the ideas explored in previous sections and rework them into a novel contribution to the politics of
+copyright and creativity.
 
@@
 few are as tractable to complexity theory's techniques. Sagan and Borges may have written fiction that explores the implications
-of algorithmic creation, but it would be difficult to analyse 'Contact' and 'The Library of Babel' through Kolmogorov's lens.
+of algorithmic creation, but it would be difficult to analyse 'Contact' and 'The Library of Babel' themselves through
+Kolmogorov's lens.
+
+Algomusicology is part of a rich tradition of information theoretical art and criticism. Music's deep structure and cultural
+significance give algomusicology great potential as a source of artistic analysis and inspiration.
 
@@
 \bibitem{Contact} Sagan, Carl: Contact
+\bibitem{Propositions as Types} Wadler, Philip.
 \bibitem{Blurred Lines} Williams, Pharrel and Thicke, Robin: Blurred Lines

### 2016-05-29 paper.tex
Break up double example.
Fix overspills.

@@
 
+\end{verbatim}
+
+And alternatively:
+
+\begin{verbatim}
   (->>
@@
 We can calculate the ratio between the literal notes of the song and the above description.
-The \verb|definitional| macro allows us to use the symbol \verb|row-row| in our fact notation, rather than
+The \verb|definitional| macro allows us to use the symbol \verb|row-row| in our fact notation, without
 having to paste in the entire expression.
@@
 (defmacro definitional [macro sym]
-  (let [value (-> sym repl/source-fn read-string last)]
+  (let [value
+          (-> sym repl/source-fn read-string last)]
     `(~macro ~value)))
@@
 (fact
-  (definitional description-length row-row) => 281
-  (definitional result-length row-row) => 2037
-  (definitional explanatory-power row-row) => 2037/281)
+  (definitional description-length row-row)
+    => 281
+  (definitional result-length row-row)
+    => 2037
+  (definitional explanatory-power row-row)
+    => 2037/281)
 \end{verbatim}
@@
   (letfn [(expand [strings]
-            (for [s strings e elements] (conj s e)))]
+            (for [s strings e elements]
+              (conj s e)))]
     (->>
@@
 (defn decompose-into-digits [n]
-  (let [[remainder quotient] ((juxt mod quot) n 10)]
+  (let [[remainder quotient]
+          ((juxt mod quot) n 10)]
     (if (zero? quotient)
@@
 
-There is nothing in the description of the \verb|copyright-infringement-song| that is in any way related to `Blurred Lines'.
+Nothing in the the \verb|copyright-infringement-song|'s description is in any way related to `Blurred Lines'.
 It is simply a straightforward musical rendering of a well-known mathematical constant derived from the decimal counting

### 2016-05-29 paper.tex
Make Gnomes' saying consistent with title.
Fix quotes.

@@
     \item Collect underpants
-    \item ?
+    \item ????
     \item Profit
@@
 
-For the Gayte-Williams-Thicke constant. I wrote a version of 'Blurred Lines' with three parts and used a three part encoding.
+For the Gayte-Williams-Thicke constant. I wrote a version of `Blurred Lines' with three parts and used a three part encoding.
 
@@
 
-Thank you to the StrangeLoop conference of 2015, which accepted the talk 'Kolmogorov Music' from which this paper derives.
+Thank you to the StrangeLoop conference of 2015, which accepted the talk `Kolmogorov Music' from which this paper derives.
 

### 2016-05-29 paper.tex
Tidy references.

@@
 
-\bibitem{Overtone} Aaron, Sam and Rose, Jeff: Overtone (\url{http://overtone.github.io})
-\bibitem{Anti EP} Autechre: Anti EP
-\bibitem{Air on the G String} Wilhelmj, August arranging Bach, Johann Sebastian: Air on the G String
-\bibitem{The Library of Babel} Borges, Jorge Luis: The Library of Babel
-\bibitem{The construction of decimals normal in the scale of ten} Champernowne, David: The construction of decimals normal in the scale of ten
-\bibitem{Gnomes} Brady, Pam, Parker, Trey and Stone, Matt. Episode 17, season 2 of South Park
-\bibitem{Got to Give It Up} Got to Give It Up: Gaye, Marvin
-\bibitem{Leipzig} Ford, Chris: Leipzig
-\bibitem{Joseph Gallivan on pop} Gallivan, Joseph: Joseph Gallivan on pop (\url{http://www.independent.co.uk/life-style/jospeh-gallivan-on-pop-1414727.html})
-\bibitem{Clojure} Hickey, Rich: Clojure
-\bibitem{On Tables of Random Numbers}  Kolmogorov, Andrey: On Tables of Random Numbers
-\bibitem{Midje} Marick, Brian: Midje
-\bibitem{Analysis by Compression} Meredith, David: Analysis by Compression
-\bibitem{USA Today} Oldenburg, Ann: 'Blurred Lines' jury finds for Marvin Gaye (\url{http://www.usatoday.com/story/life/music/2015/03/10/blurred-lines-trial-verdict/24492431/})
-\bibitem{Contact} Sagan, Carl: Contact
-\bibitem{Propositions as Types} Wadler, Philip.
-\bibitem{Blurred Lines} Williams, Pharrel and Thicke, Robin: Blurred Lines
+\bibitem{Overtone} Aaron, Sam and Rose, Jeff: Overtone, \url{https://overtone.github.io}.
+\bibitem{Anti EP} Autechre (Rob Brown and Sean Booth): Anti EP, Warp Records, 1994.
+\bibitem{Air on the G String} Wilhelmj, August arranging Bach, Johann Sebastian: Air on the G String, late 19th century.
+\bibitem{The Library of Babel} Borges, Jorge Luis: The Library of Babel, \textit{The Garden of Forking Paths}, 1941.
+\bibitem{The construction of decimals normal in the scale of ten} Champernowne, David: The construction of decimals normal in the scale of ten, \textit{Journal of the London Mathematical Society}, 1933.
+\bibitem{Gnomes} Brady, Pam, Parker, Trey and Stone, Matt: Gnomes, Episode 17, Season 2 of \textit{South Park}, 1998.
+\bibitem{Got to Give It Up} Gaye, Marvin: Got to Give It Up, \textit{Tamla}, 1977.
+\bibitem{Leipzig} Ford, Chris: Leipzig, \url{https://github.com/ctford/leipzig}.
+\bibitem{Joseph Gallivan on pop} Gallivan, Joseph: Joseph Gallivan on pop, \textit{The Independent}, July 18, 1994.
+\bibitem{Clojure} Hickey, Rich: Clojure, \url{http://clojure.org/}
+\bibitem{On Tables of Random Numbers}  Kolmogorov, Andrey: On Tables of Random Numbers, \textit{Sankhyā Ser}, 1963.
+\bibitem{Midje} Marick, Brian: Midje, \url{https://github.com/marick/Midje}.
+\bibitem{Analysis by Compression} Meredith, David: Analysis by Compression, \textit{The Music Encoding Conference}, 2013.
+\bibitem{USA Today} Oldenburg, Ann: 'Blurred Lines' jury finds for Marvin Gaye, \textit{USA Today}, March 11, 2015.
+\bibitem{Contact} Sagan, Carl: Contact, 1985.
+\bibitem{Propositions as Types} Wadler, Philip: Propositions as Types, \textit{CACM}, 2015.
+\bibitem{Blurred Lines} Williams, Pharrel and Thicke, Robin: Blurred Lines, \textit{Star Trak Recordings}, 2013.
 

### 2016-05-29 paper.tex
Update acknowledgements.
Elucidate the copyright infringement explanation a little more.

@@
 
-The encoding is relatively simple, each four digit word in the natural number is turned into a note, two digits for duration and
+The encoding is relatively direct. Each four digit word in the natural number is turned into a note, two digits for duration and
 two digits for pitch. The two digits for duration are interpreted as a fraction, and the two digits for pitch as a midi code.
@@
 For the Gayte-Williams-Thicke constant. I wrote a version of `Blurred Lines' with three parts and used a three part encoding.
+The piece presented is actually lexicon for music of up to three parts using equal temperament and notes with simple
+fractional durations, not all possible sound art pieces.
+
+This is sufficient to clash with the vast majority of known works from a copyright perspective, though
+it is not enough fideltity to reproduce the exact feel and playing style of every known piece. However, extending the idea of
+a lexicon to binary formats like mp3 would be very possible.
 
@@
 that made this paper possible.
+
+Finally, thank you to the generous people who read through early drafts of this paper and made many valuable suggestions.
 

### 2016-05-29 paper.tex
Phrasing.

@@
 Algomusicologists and starter-uppers have a challenge in common with the Underpants Gnomes
-- we may have collected and analysed a considerable quantity of underpants/music/users, but how are we to turn that into profit?
+- we may have collected and analysed a considerable quantity of underpants/music/users, but how are we to profit from that?
 

### 2016-05-29 paper.tex
Tweak.

@@
 
-This paper will argue that it can. It will do so by reviewing existing art works that are algorithmic in nature, and
-also by using algomusicological concepts to create a new work that challenges our present conception of musical authorship and
-copyright. As befits its subject matter, this paper will incorporate conventions and style from literary essays and musicology
-papers.
+This paper will argue that it can. It will do so by reviewing existing literary and musical works that are informed by algorithmic
+thinking, and also by using algomusicological concepts to create a new work that challenges our present conception of musical
+authorship and copyright. As befits its subject matter, this paper will incorporate conventions and style from literary essays
+and musicology papers.
 
@@
 sequences of time/pitch tuples. Selecting which encoding scheme to use is less straightforward, because the choice of primitives
-can affect the complexity score. Ultimately, the choice of music theory library is difficult, somewhat subjective and
-will not be answered here.
+can affect the complexity score. Ultimately, the choice of music theory language is difficult, somewhat subjective and
+has trade-offs. I will not attempt to address this choice here as it doesn't materially impact my arguments.
 
@@
 scientists struggle with whether they are the inventors of new theories or discoverers. Philip Wadler, for example,
-argues that the lambda calculus is such a fundamental concept that it deserves to be considered a universal concept that
+argues that the lambda calculus is so fundamental that it deserves to be considered a universal concept that
 was discovered\cite{Propositions as Types}. By positing a library where any work may be found if you know where to look, Borges

### 2016-06-12 paper.tex
Improve definition of algomusicology.
Fix formatting in bibliography.

@@
 than we'd like.~\footnote{Alonzo Church developed the lambda calculus in the 1930s. Java gained lambda expressions in 2015.}
-Can algomusicology influence music?~\footnote{This paper appears to be the first reference to algomusicology. I believe the term,
-which is a portmanteau of algorave and musicology, has a self-evident definition.}
+Can algomusicology influence music?~\footnote{This paper appears to be the first reference to algomusicology. I use the term,
+which is a portmanteau of algorave and musicology, to describe the use of information theory and programming for musical analysis.}
 
@@
 \bibitem{Overtone} Aaron, Sam and Rose, Jeff: Overtone, \url{https://overtone.github.io}.
-\bibitem{Anti EP} Autechre (Rob Brown and Sean Booth): Anti EP, Warp Records, 1994.
+\bibitem{Anti EP} Autechre (Rob Brown and Sean Booth): Anti EP, \textit{Warp Records}, 1994.
 \bibitem{Air on the G String} Wilhelmj, August arranging Bach, Johann Sebastian: Air on the G String, late 19th century.
@@
 \bibitem{Analysis by Compression} Meredith, David: Analysis by Compression, \textit{The Music Encoding Conference}, 2013.
-\bibitem{USA Today} Oldenburg, Ann: 'Blurred Lines' jury finds for Marvin Gaye, \textit{USA Today}, March 11, 2015.
+\bibitem{USA Today} Oldenburg, Ann: `Blurred Lines' jury finds for Marvin Gaye, \textit{USA Today}, March 11, 2015.
 \bibitem{Contact} Sagan, Carl: Contact, 1985.

### 2016-06-12 paper.tex
Removing preprint.
Restore missing article.
Alphabetise references.
Link to Github.

@@
 % Based on the template for sigplanconf LaTeX Class by Paul C. Anagnostopoulos (paul@windfall.com)
-\documentclass[numbers, preprint]{sigplanconf}
+\documentclass[numbers]{sigplanconf}
 
@@
 David Meredith has used Kolmogorov complexity to compare the quality of musical analyses\cite{Analysis by Compression}.
-He starts by assuming that musical analysis aims to produce ``best possible explanation for musical works". If that's the case,
+He starts by assuming that musical analysis aims to produce the ``best possible explanation for musical works". If that's the case,
 how might we compare two different analyses of the same piece?
@@
 
+The full source code for the \verb|copyright-infringement-song|, along with the rest of the code samples in this paper, is
+available at \url{https://github.com/ctford/kolmogorov-music}.
+
 \acks
@@
 \bibitem{Anti EP} Autechre (Rob Brown and Sean Booth): Anti EP, \textit{Warp Records}, 1994.
-\bibitem{Air on the G String} Wilhelmj, August arranging Bach, Johann Sebastian: Air on the G String, late 19th century.
 \bibitem{The Library of Babel} Borges, Jorge Luis: The Library of Babel, \textit{The Garden of Forking Paths}, 1941.
+\bibitem{Gnomes} Brady, Pam, Parker, Trey and Stone, Matt: Gnomes, Episode 17, Season 2 of \textit{South Park}, 1998.
 \bibitem{The construction of decimals normal in the scale of ten} Champernowne, David: The construction of decimals normal in the scale of ten, \textit{Journal of the London Mathematical Society}, 1933.
-\bibitem{Gnomes} Brady, Pam, Parker, Trey and Stone, Matt: Gnomes, Episode 17, Season 2 of \textit{South Park}, 1998.
-\bibitem{Got to Give It Up} Gaye, Marvin: Got to Give It Up, \textit{Tamla}, 1977.
 \bibitem{Leipzig} Ford, Chris: Leipzig, \url{https://github.com/ctford/leipzig}.
 \bibitem{Joseph Gallivan on pop} Gallivan, Joseph: Joseph Gallivan on pop, \textit{The Independent}, July 18, 1994.
+\bibitem{Got to Give It Up} Gaye, Marvin: Got to Give It Up, \textit{Tamla}, 1977.
 \bibitem{Clojure} Hickey, Rich: Clojure, \url{http://clojure.org/}
@@
 \bibitem{Propositions as Types} Wadler, Philip: Propositions as Types, \textit{CACM}, 2015.
+\bibitem{Air on the G String} Wilhelmj, August arranging Bach, Johann Sebastian: Air on the G String, late 19th century.
 \bibitem{Blurred Lines} Williams, Pharrel and Thicke, Robin: Blurred Lines, \textit{Star Trak Recordings}, 2013.

### 2016-06-12 paper.tex
Remove prefixed import for consistency.
Add publishers to references.

@@
 (fact
-  (->> (leipzig/phrase [2/3 1/3] [0 4]) encode)
+  (->> (phrase [2/3 1/3] [0 4]) encode)
     => 23001304)
@@
 \bibitem{Anti EP} Autechre (Rob Brown and Sean Booth): Anti EP, \textit{Warp Records}, 1994.
-\bibitem{The Library of Babel} Borges, Jorge Luis: The Library of Babel, \textit{The Garden of Forking Paths}, 1941.
+\bibitem{The Library of Babel} Borges, Jorge Luis: `The Library of Babel' in The Garden of Forking Paths, \textit{Editorial Sur}, 1941.
 \bibitem{Gnomes} Brady, Pam, Parker, Trey and Stone, Matt: Gnomes, Episode 17, Season 2 of \textit{South Park}, 1998.
@@
 \bibitem{USA Today} Oldenburg, Ann: `Blurred Lines' jury finds for Marvin Gaye, \textit{USA Today}, March 11, 2015.
-\bibitem{Contact} Sagan, Carl: Contact, 1985.
-\bibitem{Propositions as Types} Wadler, Philip: Propositions as Types, \textit{CACM}, 2015.
+\bibitem{Contact} Sagan, Carl: Contact, \textit{Simon and Schuster}, 1985.
+\bibitem{Propositions as Types} Wadler, Philip: Propositions as Types, \textit{Communications of the ACM}, 2015.
 \bibitem{Air on the G String} Wilhelmj, August arranging Bach, Johann Sebastian: Air on the G String, late 19th century.

### 2016-06-12 paper.tex
Be specific about which edition of a journal has the paper.

@@
 \bibitem{Gnomes} Brady, Pam, Parker, Trey and Stone, Matt: Gnomes, Episode 17, Season 2 of \textit{South Park}, 1998.
-\bibitem{The construction of decimals normal in the scale of ten} Champernowne, David: The construction of decimals normal in the scale of ten, \textit{Journal of the London Mathematical Society}, 1933.
+\bibitem{The construction of decimals normal in the scale of ten} Champernowne, David: The construction of decimals normal in the scale of ten, \textit{Journal of the London Mathematical Society}, volume 8, 1933.
 \bibitem{Leipzig} Ford, Chris: Leipzig, \url{https://github.com/ctford/leipzig}.
@@
 \bibitem{Clojure} Hickey, Rich: Clojure, \url{http://clojure.org/}
-\bibitem{On Tables of Random Numbers}  Kolmogorov, Andrey: On Tables of Random Numbers, \textit{Sankhyā Ser}, 1963.
+\bibitem{On Tables of Random Numbers}  Kolmogorov, Andrey: On Tables of Random Numbers, \textit{Sankhyā Series A}, volume 25, 1963.
 \bibitem{Midje} Marick, Brian: Midje, \url{https://github.com/marick/Midje}.
@@
 \bibitem{Contact} Sagan, Carl: Contact, \textit{Simon and Schuster}, 1985.
-\bibitem{Propositions as Types} Wadler, Philip: Propositions as Types, \textit{Communications of the ACM}, 2015.
+\bibitem{Propositions as Types} Wadler, Philip: Propositions as Types, \textit{Communications of the ACM}, volume 58, issue 12, 2015.
 \bibitem{Air on the G String} Wilhelmj, August arranging Bach, Johann Sebastian: Air on the G String, late 19th century.

### 2016-07-23 paper.tex
Incorporate detailed feedback from reviewer 1.

@@
 Can algomusicology influence music?~\footnote{This paper appears to be the first reference to algomusicology. I use the term,
-which is a portmanteau of algorave and musicology, to describe the use of information theory and programming for musical analysis.}
+which is a portmanteau of algorithm and musicology similar to algorave, to describe the use of information theory and programming for musical analysis.}
 
@@
 
-\section{Air on the {\textbackslash}G String\cite{Air on the G String}}
+\section{Air on the {\textbackslash}G String}
 Very great quantities of data can exhibit very little complexity. Consider the following Clojure expression, which
@@
 The Kleene star is the set of all possible strings that can be built from a set of elements. Here is a function that takes a set
-of elements and enumerates the Kleene star a lazy sequence. It works by taking the strings generated thus far, appending each
+of elements and enumerates the Kleene star as a lazy sequence. It works by taking the strings generated thus far, appending each
 element to each string and then repeating the process. This results in an infinite lazy sequence of strings of ever increasing
@@
 
-For the Gayte-Williams-Thicke constant. I wrote a version of `Blurred Lines' with three parts and used a three part encoding.
+For the Gayte-Williams-Thicke constant, I wrote a version of `Blurred Lines' with three parts and used a three part encoding.
 The piece presented is actually lexicon for music of up to three parts using equal temperament and notes with simple
@@
 \bibitem{Propositions as Types} Wadler, Philip: Propositions as Types, \textit{Communications of the ACM}, volume 58, issue 12, 2015.
-\bibitem{Air on the G String} Wilhelmj, August arranging Bach, Johann Sebastian: Air on the G String, late 19th century.
 \bibitem{Blurred Lines} Williams, Pharrel and Thicke, Robin: Blurred Lines, \textit{Star Trak Recordings}, 2013.

### 2016-07-23 paper.tex
Incorporate detailed feedback from reviewer 3.

@@
 Though storing such a string would require roughly a petabyte of memory, representing it indirectly as a computation
-takes very little space at all. That's roughly the size all music ever recorded,
-described in less than a half a tweet.~\footnote{Based on the iTunes library featuring approximately 50 million songs
-of approximately 4 megabytes each, and assuming it represents approximately a fifth of all recorded music. Tweets are
-restricted to 140 characters.}
+takes very little space at all. That is roughly five times the the size of the entire iTunes library,
+described in less than a half a tweet.~\footnote{Based on the the iTunes library featuring approximately 50 million songs
+of approximately 4 megabytes each. Tweets are restricted to 140 characters.}
 

### 2016-07-23 paper.tex
s/Algomusicology/Computational musicology/g

@@
 
-\title{Algomusicology, ????, Profit}
+\title{Computational musicology, ????, Profit}
 %\subtitle{Subtitle Text, if any}
@@
 \begin{abstract}
-In this paper I propose a novel method for converting algomusicology into profit. While my particular example
+In this paper I propose a novel method for converting computational musicology into profit. While my particular example
 is tongue-in-cheek, it shows that algorithmic composition and analysis can help us deconstruct and disrupt
@@
 
-Less glibly, is algomusicology doomed to be a mere observer and explainer of musical practice, or might it become an
+Less glibly, is computational musicology doomed to be a mere observer and explainer of musical practice, or might it become an
 active participant in the conversation? Computer science is able to influence the software industry, though that might take longer
 than we'd like.~\footnote{Alonzo Church developed the lambda calculus in the 1930s. Java gained lambda expressions in 2015.}
-Can algomusicology influence music?~\footnote{This paper appears to be the first reference to algomusicology. I use the term,
-which is a portmanteau of algorithm and musicology similar to algorave, to describe the use of information theory and programming for musical analysis.}
+Can computational musicology influence music?
 
@@
 \begin{enumerate}
-    \item Algomusicology
+    \item Computational musicology
     \item Copyright litigation
@@
 
-More seriously, this paper attempts to show that algomusicology can meaningfully shed light on how music works. Also, as in
+More seriously, this paper attempts to show that computational musicology can meaningfully shed light on how music works. Also, as in
 the case of the \verb|copyright-infringement-song|, complexity theory can contribute ideas that are artistically interesting.
-In other words, algomusicology can contribute to musical practice, not just explain it.
+In other words, computational musicology can contribute to musical practice, not just explain it.
 
@@
 
-Algomusicology is part of a rich tradition of information theoretical art and criticism. Music's deep structure and cultural
-significance give algomusicology great potential as a source of artistic analysis and inspiration.
+Computational musicology is part of a rich tradition of information theoretical art and criticism. Music's deep structure and cultural
+significance give computational musicology great potential as a source of artistic analysis and inspiration.
 

### 2016-07-23 paper.tex
Clean up some algomusicology references and add more important references.

@@
 A common interpretation of the Gnomes' business is as a satire on Silicon Valley startups.
-Algomusicologists and starter-uppers have a challenge in common with the Underpants Gnomes
+Computational musicologists and starter-uppers have a challenge in common with the Underpants Gnomes
 - we may have collected and analysed a considerable quantity of underpants/music/users, but how are we to profit from that?
@@
 This paper will argue that it can. It will do so by reviewing existing literary and musical works that are informed by algorithmic
-thinking, and also by using algomusicological concepts to create a new work that challenges our present conception of musical
+thinking, and also by using computational musicological concepts to create a new work that challenges our present conception of musical
 authorship and copyright. As befits its subject matter, this paper will incorporate conventions and style from literary essays
@@
 \cite{Joseph Gallivan on pop}
-In other words, as every bar features a unique beat, `Flutter' does not match the government's algomusicological description
+In other words, as every bar features a unique beat, `Flutter' does not match the government's computational musicological description
 of ``repetitive beats".
@@
 
-Both legislators and artists are clearly taking algomusicological positions. The government attempted to construct the set
+Both legislators and artists are clearly taking computational musicological positions. The government attempted to construct the set
 of all rave musics using a complexity characterisation. Autechre responded with what amounts to a diagonal argument, demonstrating
@@
 a universal piece of music, any work published subsequent to it infringes on its copyright.~\footnote{I am not a lawyer.
-Do not rely on my legal advice.} In order to convert our algomusicological understanding into profit, we simply have to sue the composers
+Do not rely on my legal advice.} In order to convert our computational musicology understanding into profit, we simply have to sue the composers
 of every marginally successful musical work from now until they fix the law.
@@
 \bibitem{The construction of decimals normal in the scale of ten} Champernowne, David: The construction of decimals normal in the scale of ten, \textit{Journal of the London Mathematical Society}, volume 8, 1933.
+\bibitem{Computational Musicology} Eduardo Coutinho, Marcelo Gimenes, Joao M. Martins and Eduardo R. Miranda: TODO. 
+\bibitem{Three Paradigms of Computer Science} Eden, Amnon. TODO.
 \bibitem{Leipzig} Ford, Chris: Leipzig, \url{https://github.com/ctford/leipzig}.
@@
 \bibitem{Midje} Marick, Brian: Midje, \url{https://github.com/marick/Midje}.
+\bibitem{The Digital Computer as a Musical Instrument} Mathews, M. V., \textid{Science}, 1963. TODO.
 \bibitem{Analysis by Compression} Meredith, David: Analysis by Compression, \textit{The Music Encoding Conference}, 2013.
+\bibitem{Music, Mind and Meaning} Minsky, Marvin. 1981.
 \bibitem{USA Today} Oldenburg, Ann: `Blurred Lines' jury finds for Marvin Gaye, \textit{USA Today}, March 11, 2015.

### 2016-07-24 paper.tex
Add section on programming paradigms.

@@
 
+\section{Programming Paradigms}
+
+Computational musicology is unusual in that it transgresses the barrier between what C. P. Snow called the two cultures of academia
+- the sciences and the humanities\cite{Two Cultures}. Programming has conventionally been placed with the sciences, yet music is a
+creative endevour usually understood as part of the humanities. In order to understand how computational musicology might
+contribute to music, we have to examine this paradox.
+
+Amnon Eden classifies the way that computer scientists think about their craft into rationalist, technocratic and scientific paradigms\cite{Three Paradigms}.
+These conceptual models position programmers as mathematicians, engineers or scientists respectively. They vary in how they
+produce knowledge, but all three belong to Snow's scientific culture. None of them value or use literary methods.
+
+To properly understand computational musicology, let us contrast with computational physics. Computational physics papers cannot
+influence natural phenomena because physics cannot influence natural phenomena.
+There is an inviolable barrier between the subject (physics) and
+the object (natural phenomena), so the field of study cannot contribute to its object. Planets orbited the sun long before
+Copernicus presented a mathematical model of heliocentrism. Kepler's elliptical orbits did not consist of a new and improved way
+for celestial bodies to move. Even Galileo's emperical observations were not able to provoke reform of the solar system itself.
+
+While the history of scientific ideas is important and fascinating, they are entirely immaterial to the natural phenomena
+themselves, who are oblivious to observation (quantum effects notwithstanding). That is not true of literary or musical criticism.
+Musicians, authors and their audiences read critical writing about music and literature. Both the production and the consumption
+of art take place in a field of ideas at least partially shaped by critics. Criticism is an active participant in literary and
+musical discourse.
+
+Marvin Minksy recognises this problem in an essay called `Music, Mind, and Meaning'. He suggests that computational
+musicologists ``would like to study Mozart's music the way scientists analyze the spectrum of a distant star``, but that music
+is not the kind of object that can be studied ``uninfluenced by custom or constraint of commerce"\cite{Music, Mind and Meaning}.
+I deliberately refer to Minsky's work as an essay and not as a paper. It does not conform to the conventions of a scientific
+or mathematical paper. He uses the first person. He speculates. He draws connections that he cannot mathematically formalise.
+He makes painstaking reference to the details of a specific artistic work (Beethoven's Fifth). He states no theorems.
+
+This paper/essay attempts to resolve the tension that Minsky observed between a scientific and cultural approach to musical study
+by beginning with complexity theory and then building upon that to consider literary and musical works. The informal and literary
+styles is not just for fun (though I hope that it is that), but is also attempt to show how computational musicology might
+function as a genuine cross-cultural study between the two cultures of the sciences and the humanities.
+
 \section{Air on the {\textbackslash}G String}
+To view music within Eden's scientific paradigm, we might begin by understanding music as data.
 Very great quantities of data can exhibit very little complexity. Consider the following Clojure expression, which
@@
 
-More seriously, this paper attempts to show that computational musicology can meaningfully shed light on how music works. Also, as in
+More seriously, this paper attempts to show that computational musicology can meaningfully shed light on how music functions.
+Also, as in
 the case of the \verb|copyright-infringement-song|, complexity theory can contribute ideas that are artistically interesting.
-In other words, computational musicology can contribute to musical practice, not just explain it.
+In other words, computational musicology can contribute to musical practice, not just explain it. This is possible because music
+is a cultural phenomenon, unlike other fields to which computational methods have been applied like physics.
 
@@
 
-Computational musicology is part of a rich tradition of information theoretical art and criticism. Music's deep structure and cultural
-significance give computational musicology great potential as a source of artistic analysis and inspiration.
+Computational musicology is part of a rich tradition of information theoretical art and criticism. Music's deep structure and
+cultural significance give computational musicology great potential as a source of artistic analysis and inspiration.
+This paper represents a self-evidencing claim that computational musicology can contribute to musical ideas and appreciation.
 
@@
 \bibitem{Computational Musicology} Eduardo Coutinho, Marcelo Gimenes, Joao M. Martins and Eduardo R. Miranda: TODO. 
-\bibitem{Three Paradigms of Computer Science} Eden, Amnon. TODO.
+\bibitem{Three Paradigms} Eden, Amnon. TODO.
 \bibitem{Leipzig} Ford, Chris: Leipzig, \url{https://github.com/ctford/leipzig}.
@@
 \bibitem{Contact} Sagan, Carl: Contact, \textit{Simon and Schuster}, 1985.
+\bibitem{Two Cultures} Snow, CP. TODO
 \bibitem{Propositions as Types} Wadler, Philip: Propositions as Types, \textit{Communications of the ACM}, volume 58, issue 12, 2015.

### 2016-07-24 paper.tex
Reference online Library of Babel.

@@
 
+Borges' information theoretical conceit appeals to programmers who want to convert his ideas into executable code.
+A good example is the online Library of Babel, which includes a helpful search function for any substring that might be found
+within\cite{Online Library of Babel}. For example, the preceding paragraph of this paper can be found on page 389 of a book
+entitled `uooh.t.a ,mhentjczdb'.
+
 \section{Contact}
@@
 \bibitem{Overtone} Aaron, Sam and Rose, Jeff: Overtone, \url{https://overtone.github.io}.
+\bibitem{Online Library of Babel} Basile, Jonathan. TODO
 \bibitem{Anti EP} Autechre (Rob Brown and Sean Booth): Anti EP, \textit{Warp Records}, 1994.
@@
 \bibitem{Midje} Marick, Brian: Midje, \url{https://github.com/marick/Midje}.
-\bibitem{The Digital Computer as a Musical Instrument} Mathews, M. V., \textid{Science}, 1963. TODO.
+\bibitem{The Digital Computer as a Musical Instrument} Mathews, M. V., \textit{Science}, 1963. TODO.
 \bibitem{Analysis by Compression} Meredith, David: Analysis by Compression, \textit{The Music Encoding Conference}, 2013.

### 2016-07-24 paper.tex
Fill out references.

@@
 \bibitem{Overtone} Aaron, Sam and Rose, Jeff: Overtone, \url{https://overtone.github.io}.
-\bibitem{Online Library of Babel} Basile, Jonathan. TODO
+\bibitem{Online Library of Babel} Basile, Jonathan: \verb|libraryofbabel.info|, \url{https://libraryofbabel.info}.
 \bibitem{Anti EP} Autechre (Rob Brown and Sean Booth): Anti EP, \textit{Warp Records}, 1994.
@@
 \bibitem{Computational Musicology} Eduardo Coutinho, Marcelo Gimenes, Joao M. Martins and Eduardo R. Miranda: TODO. 
-\bibitem{Three Paradigms} Eden, Amnon. TODO.
+\bibitem{Three Paradigms} Eden, Amnon, Three Paradigms of Computer Science, \textit{Minds and Machines}, volume 17, number 2, July, 2007.
 \bibitem{Leipzig} Ford, Chris: Leipzig, \url{https://github.com/ctford/leipzig}.
@@
 \bibitem{Contact} Sagan, Carl: Contact, \textit{Simon and Schuster}, 1985.
-\bibitem{Two Cultures} Snow, CP. TODO
+\bibitem{Two Cultures} Snow, Charles Percy: The Two Cultures and the Scientific Revolution, \textit{Cambridge University Press}, 1959.
 \bibitem{Propositions as Types} Wadler, Philip: Propositions as Types, \textit{Communications of the ACM}, volume 58, issue 12, 2015.

### 2016-07-24 paper.tex
Fix Minsky references.

@@
 Marvin Minksy recognises this problem in an essay called `Music, Mind, and Meaning'. He suggests that computational
-musicologists ``would like to study Mozart's music the way scientists analyze the spectrum of a distant star``, but that music
-is not the kind of object that can be studied ``uninfluenced by custom or constraint of commerce"\cite{Music, Mind and Meaning}.
+musicologists ``would like to study Mozart's music the way scientists analyze the spectrum of a distant star", but that music
+is not the kind of object that can be studied ``uninfluenced by custom or constraint of commerce"\cite{Music Mind and Meaning}.
 I deliberately refer to Minsky's work as an essay and not as a paper. It does not conform to the conventions of a scientific
@@
 \bibitem{Analysis by Compression} Meredith, David: Analysis by Compression, \textit{The Music Encoding Conference}, 2013.
-\bibitem{Music, Mind and Meaning} Minsky, Marvin. 1981.
+\bibitem{Music Mind and Meaning} Minsky, Marvin. 1981.
 \bibitem{USA Today} Oldenburg, Ann: `Blurred Lines' jury finds for Marvin Gaye, \textit{USA Today}, March 11, 2015.

### 2016-07-24 paper.tex
Incremental edit.

@@
 These conceptual models position programmers as mathematicians, engineers or scientists respectively. They vary in how they
-produce knowledge, but all three belong to Snow's scientific culture. None of them value or use literary methods.
+produce knowledge, but all three belong to Snow's scientific culture. None value or use literary methods.
 
-To properly understand computational musicology, let us contrast with computational physics. Computational physics papers cannot
+To properly understand computational musicology, let us start with an example of computational methods that do not mix Snow's
+cultural categories. Computational physics papers cannot
 influence natural phenomena because physics cannot influence natural phenomena.
 There is an inviolable barrier between the subject (physics) and
-the object (natural phenomena), so the field of study cannot contribute to its object. Planets orbited the sun long before
-Copernicus presented a mathematical model of heliocentrism. Kepler's elliptical orbits did not consist of a new and improved way
-for celestial bodies to move. Even Galileo's emperical observations were not able to provoke reform of the solar system itself.
+the object (natural phenomena), so the field of study cannot interact with its object.
+Kepler's elliptical orbits improved our understanding of the motions of celestial bodies, but the planets themselves
+remained unaffected.
 
@@
 
-Marvin Minksy recognises this problem in an essay called `Music, Mind, and Meaning'. He suggests that computational
+Marvin Minksy recognises this problem in an essay called `Music, Mind and Meaning'. He suggests that computational
 musicologists ``would like to study Mozart's music the way scientists analyze the spectrum of a distant star", but that music
 is not the kind of object that can be studied ``uninfluenced by custom or constraint of commerce"\cite{Music Mind and Meaning}.
+
 I deliberately refer to Minsky's work as an essay and not as a paper. It does not conform to the conventions of a scientific
 or mathematical paper. He uses the first person. He speculates. He draws connections that he cannot mathematically formalise.
-He makes painstaking reference to the details of a specific artistic work (Beethoven's Fifth). He states no theorems.
+He engages deeply with the detail of an individual artistic work (Beethoven's fifth symphony). He states no theorems, though he
+does propose a model of musical perception. A conventional scientific paper would not have allowed him to express the same breadth 
+of insight.
 
@@
 \section{Air on the {\textbackslash}G String}
-To view music within Eden's scientific paradigm, we might begin by understanding music as data.
+To return to Eden's scientific paradigm for a moment, we might begin by understanding music as data.
 Very great quantities of data can exhibit very little complexity. Consider the following Clojure expression, which
@@
 
-Through his Library of Babel, Borges is playing with our notions of invention versus discovery. Mathematicians and computer
+Through the Library of Babel, Borges plays with our notions of invention versus discovery. Mathematicians and computer
 scientists struggle with whether they are the inventors of new theories or discoverers. Philip Wadler, for example,
@@
 a universal piece of music, any work published subsequent to it infringes on its copyright.~\footnote{I am not a lawyer.
-Do not rely on my legal advice.} In order to convert our computational musicology understanding into profit, we simply have to sue the composers
-of every marginally successful musical work from now until they fix the law.
+Do not rely on my legal advice.} In order to convert our computational musicology understanding into profit, we simply have to
+sue the composers of every marginally successful musical work from now until they fix the law.
 
@@
 cultural significance give computational musicology great potential as a source of artistic analysis and inspiration.
-This paper represents a self-evidencing claim that computational musicology can contribute to musical ideas and appreciation.
+This paper represents a self-supporting claim that computational musicology can contribute to musical ideas and appreciation as
+a form of creative criticism.
 

### 2016-07-24 paper.tex
Make the appendix a regular section.
Cite plaguerism detection stuff.

@@
 As the Champernowne word's digits are predictable, I am able to skip ahead to any part of the song I choose. Here
-is the value of \verb|skip-to| that results in a passable version of `Blurred Lines'.~\footnote{The encoding scheme is chosen
-to be reversible, which allowed me to determine where in the Champernowne word `Blurred Lines' would occur. Full details are in the appendix and the accompanying code.}
+is the input to \verb|skip-to| that results in a passable version of `Blurred Lines'.~\footnote{The encoding scheme is chosen
+to be reversible, which allowed me to determine where in the Champernowne word `Blurred Lines' would occur. Full details are in the next section.}
 
@@
 Do not rely on my legal advice.} In order to convert our computational musicology understanding into profit, we simply have to
-sue the composers of every marginally successful musical work from now until they fix the law.
+sue the composers of every marginally successful musical work from now until they fix the law. Previous works have used
+complexity analyses to detect copyright infringement\cite{Intrinsic Plaguerism Detection}. Here we take that one step further
+and use complexity theory to cause copyright infringement.
 
-\section{Conclusion}
-
-On one level, the puzzle posed by the title of this paper has a straightforward solution:
-\begin{enumerate}
-    \item Computational musicology
-    \item Copyright litigation
-    \item Profit!
-\end{enumerate}
-
-More seriously, this paper attempts to show that computational musicology can meaningfully shed light on how music functions.
-Also, as in
-the case of the \verb|copyright-infringement-song|, complexity theory can contribute ideas that are artistically interesting.
-In other words, computational musicology can contribute to musical practice, not just explain it. This is possible because music
-is a cultural phenomenon, unlike other fields to which computational methods have been applied like physics.
-
-As an artform, music is an ideal subject for complexity analysis. Other media can also engage with complexity theory, but
-few are as tractable to complexity theory's techniques. Sagan and Borges may have written fiction that explores the implications
-of algorithmic creation, but it would be difficult to analyse 'Contact' and 'The Library of Babel' themselves through
-Kolmogorov's lens.
-
-Computational musicology is part of a rich tradition of information theoretical art and criticism. Music's deep structure and
-cultural significance give computational musicology great potential as a source of artistic analysis and inspiration.
-This paper represents a self-supporting claim that computational musicology can contribute to musical ideas and appreciation as
-a form of creative criticism.
-
-\appendix
 \section{Encoding the Champernowne Constant}
@@
 
+\section{Conclusion}
+
+On one level, the puzzle posed by the title of this paper has a straightforward solution:
+\begin{enumerate}
+    \item Computational musicology
+    \item Copyright litigation
+    \item Profit!
+\end{enumerate}
+
+More seriously, this paper attempts to show that computational musicology can meaningfully shed light on how music functions.
+Also, as in
+the case of the \verb|copyright-infringement-song|, complexity theory can contribute ideas that are artistically interesting.
+In other words, computational musicology can contribute to musical practice, not just explain it. This is possible because music
+is a cultural phenomenon, unlike other fields to which computational methods have been applied like physics.
+
+As an artform, music is an ideal subject for complexity analysis. Other media can also engage with complexity theory, but
+few are as tractable to complexity theory's techniques. Sagan and Borges may have written fiction that explores the implications
+of algorithmic creation, but it would be difficult to analyse 'Contact' and 'The Library of Babel' themselves through
+Kolmogorov's lens.
+
+Computational musicology is part of a rich tradition of information theoretical art and criticism. Music's deep structure and
+cultural significance give computational musicology great potential as a source of artistic analysis and inspiration.
+This paper represents a self-supporting claim that computational musicology can contribute to musical ideas and appreciation as
+a form of creative criticism.
+
 \acks
@@
 \bibitem{Contact} Sagan, Carl: Contact, \textit{Simon and Schuster}, 1985.
+\bibitem{Intrinsic Plaguerism Detection} Seaward, Leanne and Matwin, Stan: Intrinsic Plagiarism Detection using Complexity Analysis, \textit{PAN'09}, 2009.
 \bibitem{Two Cultures} Snow, Charles Percy: The Two Cultures and the Scientific Revolution, \textit{Cambridge University Press}, 1959.

### 2016-07-24 paper.tex
Incorporate plaguerism stuff and computer-as-instrument stuff.

@@
 the similarity between songs and not, for example, on a conditional Kolmogorov complexity analysis of the distance between
-the two compositions.
+the two compositions, for example in the manner Seaward and Matwin suggest for textual plaguerism\cite{Intrinsic Plaguerism Detection}.
 
-As a response to this situation, I decided to compose a track that would infringe on the copyright of both songs. The following
-piece decodes the Champernowne word into music.
+As a response to this situation, I decided to compose a track that would infringe on the copyright of both songs. In doing so, I
+am participating in a long tradition of computer-aided composition, described for example in M. V. Mathews' 1963 paper
+``The Digital Computer as a Musical Instrument"\cite{The Digital Computer as a Musical Instrument}.
+
+The following piece decodes the Champernowne word into music.
 
@@
 It is simply a straightforward musical rendering of a well-known mathematical constant derived from the decimal counting
-system.
+system. This is a degenerate case of M. V. Mathews' vision that music coding would allow a composer to
+``write directly in parameters that are much more
+closely related to his musical objectives, letting the machine generate the individual
+notes"\cite{The Digital Computer as a Musical Instrument}.
 
@@
 Do not rely on my legal advice.} In order to convert our computational musicology understanding into profit, we simply have to
-sue the composers of every marginally successful musical work from now until they fix the law. Previous works have used
-complexity analyses to detect copyright infringement\cite{Intrinsic Plaguerism Detection}. Here we take that one step further
-and use complexity theory to cause copyright infringement.
+sue the composers of every marginally successful musical work from now until they fix the law. Previous works such as Seaward
+and Matwin's paper have used complexity analyses to detect copyright infringement\cite{Intrinsic Plaguerism Detection}.
+Here we have taken that one step further and use complexity theory to cause copyright infringement.
 

### 2016-07-24 paper.tex
Fix some references and the introduction.

@@
 is tongue-in-cheek, it shows that algorithmic composition and analysis can help us deconstruct and disrupt
-traditional notions of musical authorship.
+traditional notions of musical authorship. I adopt literary modes of analysis and presentation, which I motivate by
+arguing that music is a cultural and artistic phenomenon rather than a natural one.
 \end{abstract}
@@
 This paper will argue that it can. It will do so by reviewing existing literary and musical works that are informed by algorithmic
-thinking, and also by using computational musicological concepts to create a new work that challenges our present conception of musical
-authorship and copyright. As befits its subject matter, this paper will incorporate conventions and style from literary essays
-and musicology papers.
+thinking, and also by using computational musicological concepts to create a new work that challenges our present conception of
+musical authorship and copyright. As befits its subject matter, this paper will incorporate conventions and style from literary
+essays.
+
+This is a stylistic and a methodological departure from many previous papers on computational musicology. For example, Eduardo
+Coutinho, Marcelo Gimenes, Joao M. Martins and Eduardo R. Miranda write that ``computational musicology is broadly defined as the
+study of Music by means of computer modelling and simulation"\cite{Computational Musicology}. Coutinho et al. approach
+computational musicology from a mathematical and a scientific perspective, but this paper will take a mathematical foundation
+and build on it with analysis and criticism more common to the literary field.
 
@@
 
-Marvin Minksy recognises this problem in an essay called `Music, Mind and Meaning'. He suggests that computational
+Marvin Minksy recognises this problem in an essay called `Music, Mind, and Meaning'. He suggests that computational
 musicologists ``would like to study Mozart's music the way scientists analyze the spectrum of a distant star", but that music
@@
 
-What's more, every other song is also somewhere in there. Past, present and future compositions already exist somewhere in
-the depths of this infinite piece.
+Here we have let the machine generate \textit{all} the individual notes. Every song exists somewhere in there. Past, present and
+future compositions already exist somewhere in the depths of this infinite piece.
 
@@
 \bibitem{The construction of decimals normal in the scale of ten} Champernowne, David: The construction of decimals normal in the scale of ten, \textit{Journal of the London Mathematical Society}, volume 8, 1933.
-\bibitem{Computational Musicology} Eduardo Coutinho, Marcelo Gimenes, Joao M. Martins and Eduardo R. Miranda: TODO.
+\bibitem{Computational Musicology} Eduardo Coutinho, Marcelo Gimenes, Joao M.
+Martins and Eduardo R.
+Miranda: Computational	Musicology:	An Artificial Life Approach \textit{Proceedings of the 2nd Portuguese Workshop on Artiﬁcial Life and Evolutionary Algorithms Workshop}, 2005.
 \bibitem{Three Paradigms} Eden, Amnon, Three Paradigms of Computer Science, \textit{Minds and Machines}, volume 17, number 2, July, 2007.
@@
 \bibitem{Midje} Marick, Brian: Midje, \url{https://github.com/marick/Midje}.
-\bibitem{The Digital Computer as a Musical Instrument} Mathews, M. V., \textit{Science}, 1963. TODO.
+\bibitem{The Digital Computer as a Musical Instrument} Mathews, Max Vernon, \textit{Science}, volume 142, number 11, 1963.
 \bibitem{Analysis by Compression} Meredith, David: Analysis by Compression, \textit{The Music Encoding Conference}, 2013.
-\bibitem{Music Mind and Meaning} Minsky, Marvin. 1981.
+\bibitem{Music Mind and Meaning} Minsky, Marvin: Music, Mind, and Meaning, \textit{Computer Music Journal}, volume 5, number 3, Fall 1981.
 \bibitem{USA Today} Oldenburg, Ann: `Blurred Lines' jury finds for Marvin Gaye, \textit{USA Today}, March 11, 2015.

### 2016-07-24 paper.tex
Iterate on the paradigm stuff.

@@
 Computational musicology is unusual in that it transgresses the barrier between what C. P. Snow called the two cultures of academia
-- the sciences and the humanities\cite{Two Cultures}. Programming has conventionally been placed with the sciences, yet music is a
+- the scientific and the literary\cite{Two Cultures}. Programming has conventionally been placed with the sciences, yet music is a
 creative endevour usually understood as part of the humanities. In order to understand how computational musicology might
@@
 
-Amnon Eden classifies the way that computer scientists think about their craft into rationalist, technocratic and scientific paradigms\cite{Three Paradigms}.
-These conceptual models position programmers as mathematicians, engineers or scientists respectively. They vary in how they
+Amnon Eden classifies the way that computer scientists conceptualise their craft into rationalist, technocratic and scientific paradigms\cite{Three Paradigms}.
+These models position programmers as mathematicians, engineers or scientists respectively. They vary in how they
 produce knowledge, but all three belong to Snow's scientific culture. None value or use literary methods.
@@
 
-Marvin Minksy recognises this problem in an essay called `Music, Mind, and Meaning'. He suggests that computational
+Marvin Minksy recognises this problem in an essay called `Music, Mind, and Meaning'. He observes that computational
 musicologists ``would like to study Mozart's music the way scientists analyze the spectrum of a distant star", but that music
@@
 
-This paper/essay attempts to resolve the tension that Minsky observed between a scientific and cultural approach to musical study
-by beginning with complexity theory and then building upon that to consider literary and musical works. The informal and literary
-styles is not just for fun (though I hope that it is that), but is also attempt to show how computational musicology might
-function as a genuine cross-cultural study between the two cultures of the sciences and the humanities.
+Coutinho et al. resolve this ``puzzling old problem" a different way. They observe that while in biology ``fossils can be studied
+to understand the
+past and evolution of species", music lacks a corresponding natural object for them to base their research
+upon\cite{Computational Musicology}. Their solution is to turn to modelling and simulation as a substitute that allows them
+to make their work "scientifically sound".
+
+This paper/essay however, attempts to resolve the tension that Minsky observed between a scientific and cultural approach to
+musical study by beginning with complexity theory and then building upon that to consider literary and musical works. The
+informal and literary style is not just for fun (though I hope that it is that), but is also attempt to show how computational
+musicology might function as a genuine cross-cultural study between the two cultures of the sciences and the humanities.
 
@@
 
-The full source code for the \verb|copyright-infringement-song|, along with the rest of the code samples in this paper, is
-available at \url{https://github.com/ctford/kolmogorov-music}.
-
 \section{Conclusion}
@@
 few are as tractable to complexity theory's techniques. Sagan and Borges may have written fiction that explores the implications
-of algorithmic creation, but it would be difficult to analyse 'Contact' and 'The Library of Babel' themselves through
+of algorithmic creation, but it would be difficult to analyse `Contact' and `The Library of Babel' themselves through
 Kolmogorov's lens.
@@
 a form of creative criticism.
+
+The full source code for the \verb|copyright-infringement-song|, along with the rest of the code samples in this paper, is
+available at \url{https://github.com/ctford/kolmogorov-music}.
 

### 2016-07-25 paper.tex
Fix quotes.
Don't hide anything in the abstract.

@@
 \begin{abstract}
-In this paper I propose a novel method for converting computational musicology into profit. While my particular example
-is tongue-in-cheek, it shows that algorithmic composition and analysis can help us deconstruct and disrupt
-traditional notions of musical authorship. I adopt literary modes of analysis and presentation, which I motivate by
+In this paper I examine the relationship of complexity theory and disjunctive sequences to music, music-generating programs and
+literary works. I then apply the theory to devising a program to generate an infinite `copyright infringement song' that contains
+all other songs within it. I adopt literary modes of analysis and presentation, which I motivate by
 arguing that music is a cultural and artistic phenomenon rather than a natural one.
@@
 upon\cite{Computational Musicology}. Their solution is to turn to modelling and simulation as a substitute that allows them
-to make their work "scientifically sound".
+to make their work ``scientifically sound".
 

### 2016-07-25 paper.tex
Mention the incompleteness theorem.
Wordsmith the abstract.

@@
 In this paper I examine the relationship of complexity theory and disjunctive sequences to music, music-generating programs and
-literary works. I then apply the theory to devising a program to generate an infinite `copyright infringement song' that contains
+literary works. I then apply these ideas by devising a program to generate an infinite `copyright infringement song' that contains
 all other songs within it. I adopt literary modes of analysis and presentation, which I motivate by
@@
 
-Instead, I devised an encoding between the natural numbers and a piece of music. This allowed me to start with the music, encode
-it and therefore discover the constant. Playing the Champernowne Constant as music is the reverse process.
+Instead, I devised an encoding between the natural numbers and a piece of music, a technique often known as a G{\"o}del numbering
+after Kurt G{\"o}del's famous incompleteness theorem. This allowed me to start with the music, encode it and therefore discover the
+constant. Playing the Champernowne Constant as music is the reverse process.
 

### 2016-07-25 paper.tex
Clarify a paragraph.

@@
 Coutinho, Marcelo Gimenes, Joao M. Martins and Eduardo R. Miranda write that ``computational musicology is broadly defined as the
-study of Music by means of computer modelling and simulation"\cite{Computational Musicology}. Coutinho et al. approach
-computational musicology from a mathematical and a scientific perspective, but this paper will take a mathematical foundation
-and build on it with analysis and criticism more common to the literary field.
+study of Music by means of computer modelling and simulation"\cite{Computational Musicology}, a description that does not admit
+literary analysis. While Coutinho et al. approach computational musicology from a mathematical and a scientific perspective,
+I will take a mathematical foundation and build on it with analysis and criticism more common to the literary field.
 

### 2016-07-31 paper.tex
Update thanks.
Avoid repeated phrase.

@@
 the similarity between songs and not, for example, on a conditional Kolmogorov complexity analysis of the distance between
-the two compositions, for example in the manner Seaward and Matwin suggest for textual plaguerism\cite{Intrinsic Plaguerism Detection}.
+the two compositions, as Seaward and Matwin suggest for textual plaguerism\cite{Intrinsic Plaguerism Detection}.
 
@@
 
-Finally, thank you to the generous people who read through early drafts of this paper and made many valuable suggestions.
+Finally, thank you to the generous people who read drafts of this paper and made many valuable suggestions.
 

### 2016-07-31 paper.tex
Strange Loop has a space.
Cite Algorave.

@@
 
-Coutinho et al. resolve this ``puzzling old problem" a different way. They observe that while in biology ``fossils can be studied
-to understand the
+Coutinho et al. resolve what they refer to as the ``puzzling old problem" a different way. They observe that while in biology
+``fossils can be studied to understand the
 past and evolution of species", music lacks a corresponding natural object for them to base their research
 upon\cite{Computational Musicology}. Their solution is to turn to modelling and simulation as a substitute that allows them
-to make their work ``scientifically sound".
+to make their work ``scientifically sound" (their words).
 
-This paper/essay however, attempts to resolve the tension that Minsky observed between a scientific and cultural approach to
-musical study by beginning with complexity theory and then building upon that to consider literary and musical works. The
+On a practical level, algorave musicians are already well advanced in finding a solution to the ``problem" of reconciling
+computation with creative practice\cite{Algorave}. These performers generate music by writing code in front of a live audience.
+They explore the
+potential and the limits of programming as a musical instrument. For them, live coding is a challenge of language and expression.
+If the praxis of programming and musical performance can be fruitfully combined, then surely literary and scientific theory
+might also be brought together.
+
+This paper/essay attempts to resolve the tension that Minsky observed between the scientific and the cultural approach to
+studying music by taking complexity theory and then building upon it to consider literary and musical works. The
 informal and literary style is not just for fun (though I hope that it is that), but is also attempt to show how computational
@@
 
-Thank you to the StrangeLoop conference of 2015, which accepted the talk `Kolmogorov Music' from which this paper derives.
+Thank you to the Strange Loop conference of 2015, which accepted the talk `Kolmogorov Music' from which this paper derives.
 
@@
 \bibitem{The construction of decimals normal in the scale of ten} Champernowne, David: The construction of decimals normal in the scale of ten, \textit{Journal of the London Mathematical Society}, volume 8, 1933.
+\bibitem{Algorave} Cheshire, Tom: Hacking meets clubbing with the `algorave', \textit{Wired}, August 29, 2013.
 \bibitem{Computational Musicology} Eduardo Coutinho, Marcelo Gimenes, Joao M.
 Martins and Eduardo R.
-Miranda: Computational	Musicology:	An Artificial Life Approach \textit{Proceedings of the 2nd Portuguese Workshop on Artiﬁcial Life and Evolutionary Algorithms Workshop}, 2005.
+Miranda: Computational	Musicology:	An Artificial Life Approach, \textit{Proceedings of the 2nd Portuguese Workshop on Artiﬁcial Life and Evolutionary Algorithms Workshop}, 2005.
 \bibitem{Three Paradigms} Eden, Amnon, Three Paradigms of Computer Science, \textit{Minds and Machines}, volume 17, number 2, July, 2007.

### 2016-07-31 paper.tex
Mild edit.

@@
 \begin{abstract}
-In this paper I examine the relationship of complexity theory and disjunctive sequences to music, music-generating programs and
-literary works. I then apply these ideas by devising a program to generate an infinite `copyright infringement song' that contains
-all other songs within it. I adopt literary modes of analysis and presentation, which I motivate by
+In this paper I examine the relationship that complexity theory and disjunctive sequences have to music, music-generating programs
+and literary works. I then apply these ideas by devising a program to generate an infinite `Copyright Infringement Song' that
+contains all other songs within it. I adopt literary modes of analysis and presentation, which I motivate by
 arguing that music is a cultural and artistic phenomenon rather than a natural one.
@@
 potential and the limits of programming as a musical instrument. For them, live coding is a challenge of language and expression.
-If the praxis of programming and musical performance can be fruitfully combined, then surely literary and scientific theory
+If the praxis of programming and musical performance can be fruitfully combined, then literary and scientific theory
 might also be brought together.
@@
 
-Using this idea, we can show that composing ``Row, row, row your boat" out of sequences of durations and pitches
+Using this idea, we can show that composing `Row, row, row your boat' out of sequences of durations and pitches
 is a better description of the piece than the raw notes. \verb|;| indicates a comment in Clojure.
@@
 
-The particularly significant compression in this way of writing ``Row, row, row your boat" is the line \verb|(canon (simple 4))|.
+The particularly significant compression in this way of writing `Row, row, row your boat' is the line \verb|(canon (simple 4))|.
 A canon is when an initial melody (often known as the dux) is accompanied by a transformation of itself (often known as the comes).
-In ``Row, row, row your boat", the comes is a copy of the dux that is delayed by four beats, a structure known as a simple canon.
+In `Row, row, row your boat', the comes is a copy of the dux that is delayed by four beats, a structure known as a simple canon.
 

### 2016-08-14 paper.tex
Add keywords.
Fix title case in heading.
Balance the columns of the final page.
Add country to affiliation.
Add category.

@@
 \usepackage{hyperref}
+\usepackage{balance}
 
@@
 \authorinfo{Chris Ford}
-           {ThoughtWorks}
+           {ThoughtWorks UK}
            {christophertford@gmail.com}
@@
 
-%\category{CR-number}{subcategory}{third-level}
+\category{J.5}{Arts and Humanities}{Arts, fine and performing}
 
-%\keywords
-%keyword1, keyword2
+\keywords
+computational musicology, musicology, complexity theory, kolmogorov complexity, literature, algorave
 
@@
 
-\section{Analysis by compression}
+\section{Analysis by Compression}
 
@@
 
+\balance
 \acks
